### 2023-05-24 NSM_mixing.tex
Creating paper repo

% NSM_mixing.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

\input{macros.tex}
\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[NSM Impact]{Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[D. Skinner et al.]{
Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
John H. Wise$^{1}$
\\
% List of institutions
$^{1}$Center for Relativistic Astrophysics, School of Physics, Georgia Institute of Technology, Atlanta, GA 30332, USA\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2023}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
The exact evolution of elements in the universe, from primordial hydrogen and helium to heavier elements like gold and platinum produced via the r-process, is still under scrutiny. The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants. The compact objects can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to take place. In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution in order to understand the impact on the second generation of stars and their metal abundances. We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time. We find that in general, a NSM leads to a significant r-process enhancement in the second generation of stars. A high explosion energy leads to all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced. When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller fraction being highly r-process enhanced. This work represents a stepping stone towards understanding how these events impact their environments and metal abundances of descendant generations of stars.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
stars: Population III -- stars: Population II -- transients: neutron star mergers -- methods: numerical
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

%====================================================================
\section{Introduction}
%====================================================================

Nucleosynthesis in the universe is a complex accounting task to undertake. Determining the source of each element of the periodic table takes great attention to the details of the particle physics and chemistry that underlies these processes. The heaviest elements of the periodic table are produced by the rapid neutron capture process, called the r-process. During this process, in regions of very high neutron densities, when the rapid bombardment of neutrons onto nuclei is faster than the rate of beta decay, nuclei can build up to produce heavy, stable elements, like Eu, Os, Ir, Pt, Th, and U. But the exact origin of this process hasn't been completely pinned down yet \citep{Cowan21, Kajino19}.

The r-process likely takes place in events that are either related to massive stars or through compact binary mergers. SNe of massive stars can produce r-process elements (see \citet{Cowan21} for a discussion on different sources). Core collapse SNe (CCSN) explosions ignited by the magnetorotational explosion model produce r-process elements in both the weak and the strong magnetic field models, with preference given to the strong magnetic field models to explain some r-process abundances of metal-poor stars \citep{Nishimura15}. Collapsars, rapidly rotating massive stars that undergo CCSN, can also produce r-process material \citep{Barnes22}. \citet{Brauer21} create a model of a population of collapsars to study these objects as the source of r-process abundances in metal-poor stars. They find that collapsars can explain the Eu abundances within metal-poor stars, although they cannot rule out NSMs as an alternative or dominant source.

In this work, we are concerned with compact binary mergers, and specifically with two NSs that merge together. Observationally, this has been confirmed. The GW170817 event was detected by LIGO, and along with it came a kilonova, a transient burst of energy powered by radioactive decay, making this event a multimessenger astronomical affair. LIGO detected a NSM with components in the mass range of $1.17 - 1.60 \Ms$ \citep{Abbott17}, and a $\gamma$-ray burst 1.7 seconds after the merger was detected by the Fermi Gamma-ray Burst Monitor \citep{Goldstein17}. This allowed for precise sky localization and a massive follow up effort from telescopes across the electromagnetic spectrum \citep[see][for an extensive review of this follow-up]{Abbott17a}. For the first time, we not only observed a NSM via GWs, but we also confirmed the association between NSMs and $\gamma$-ray bursts. Out of this massive follow-up campaign came analysis of the light curve of the kilonova in the UV, optical, and IR \citep{Drout17, Pian17}. \citet{Drout17} found that this kilonova, was in fact powered by radioactive decay of r-process elements. They estimate that $\sim 0.05 \Ms$ of enriched, r-process material must have been ejected from this event. This was the first tangible evidence that NSMs can produce a significant amount of r-process material.

Studies of the abundance of r-process elements that NSMs can produce has shown that these events can explain the r-process abundances on a global and local scale. \citet{Goriely11} used relativistic smoothed particle hydrodynamics simulations to study the ejecta of a NSM scenario. They model the merging of an equal mass NS system, $1.35 - 1.35 \Ms$, and an asymmetric system, $1.2 - 1.5 \Ms$ and use two different EoSs, one representing a ``soft'' EoS and the other a ``stiff'' EoS. A total mass yield of $\sim 10^{-3} - 10^{-2} \Ms$ is ejected in these scenarios, with the asymmetric model ejecting more material than the symmetric model. They find that nearly all galactic Eu could be explained by the yields they determined, making NSMs a promising dominant source of r-process elements.

A piece of indirect evidence comes from studying r-process abundances in metal-poor stars. \citet{Tarumi21} studied the Ba abundance, an r-process tracer element, within metal-poor stars to constrain the delay time between the formation of the binary system, and the production of r-process elements, via a NSM. In simple terms, they are investigating to see if the timing works out for the r-process enriched material to end up in metal-poor stars we see today, given their abundances. They find that as the [Fe/H] abundances increase, so do the [Ba/Mg] abundances, implicating a time delay of about 100 Myr to 1 Gyr in the r-process enrichment. \citet{Tarumi21} confidently declare that the origin of r-process elements must be sources with a time-delay baked in to the model. More locally, \citet{Bartos19} studied daughter isotopes of r-process elements found in meteorites in our solar system. Using numerical simulations of abundances in the early Solar System, they find that a NSM may have occurred $\sim 300$ pc away, 80 Myr before the formation of the Solar System, and deposited its r-process material into the pre-Solar System environment. The case for NSMs grows stronger.

The motivation for this work comes from the r-process enriched stars in Ret II. Ret II is an UFD galaxy which serves as an ideal laboratory for studying early universe star formation. These systems typically form most of their stars early in the universe, before reionization was able to suppress star formation \citep{Weisz14}. This means that these stars form in the first couple hundred million years after the Big Bang, and haven't been affected by recent mergers or enriched by recent star formation. Ret II was detected by the Dark Energy Survey \citep{Bechtol15}, whose stars have since been extensively studied \citep{Simon15, Roederer16, Ji16, Ji22}. Recently, \citet{Ji22} have found that $\sim 72\%$ of the stars in Ret II are r-process enriched, whose source could have been a prompt NSM. Since this galaxy is so isolated, it serves as an ideal case study for simulating this scenario: namely, what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?

This paper represents the proof of concept for a new NSM model that we have incorporated into Enzo, an adaptive mesh refinement cosmological simulation code. We run high-resolution cosmological simulations of a minihalo from a redshift of $z = 250$ to $z = 10$, varying the explosion energy and delay time of a NSM. We follow the material ejected into the local environment from this event into the next generation of stars to understand how this material is mixed within the environment and affects the next population of stars. The paper is structured as follows: the methods of the simulation is discussion in \ref{sec:methods}, with the added NSM model and the simulation suite described in section \ref{sec:NSM_model}. Results are presented in \ref{sec:results}, followed by a discussion in \ref{sec:discussion}. We conclude with \ref{sec:conclusion}.

%====================================================================
\section{Methods} \label{sec:methods}
%====================================================================

\subsection{Simulation set-up} \label{sec:NSM_simulation}

We use the adaptive mesh refinement, hydrodynamical cosmological simulation code \enzo{} \citep{Enzo} to run high-resolution proof-of-concept simulations of a NSM within a zoom-in simulation of a single progenitor halo, and we analyze the simulations with the analysis toolkit \yt{} \citep{yt_full_paper}. We run a total of six simulations, five with a NSM model and one without. The run without the NSM model was run first, and the following five NSM simulations are run based on the non-NSM (original) simulation. The original simulation has a domain width of 1 comoving Mpc and a root grid of $64^{3}$ cells. We use the 12-species (H2, H2+, H-, H, H+, He, He+, He++, e-, D, D+, and HD) non-equilibrium chemistry model \citep{Abel97, Anninos97}. We run this simulation to $z = 10$ and then choose the most massive halo in the box to be the target of a zoom-in simulation. We choose a Lagrangian volume around this halo, and re-initialize the simulation with two more nested grids. The highest refinement level of $l = 14$ has a minimum cell size of $8.6 \times 10^{-2}$ pc and a dark matter mass resolution of $1985 \Ms$. We refine a cell when the baryon or dark matter overdensity exceeds $3 \bar{\rho}_{\mathrm{b, DM}} \times 2^{l (3 + \epsilon)}$ where $l$ is the refinement level and $\epsilon = -0.3$ makes the refinement super-Lagrangian. We also refine around must-refine particles that are initialized in the halo's Lagrangian region, which allows for added refinement in the 8 nearest cells around moving regions up to a level of two. The Jeans length is always resolved by at least four cells. We use the cosmological parameters from the Planck Collaboration (2020) \citep{Planck18_Cosmo}: $\Omega_{\mathrm{M}} = 0.3111$, $\Omega_{\Lambda} = 0.6889$, $\Omega_{\mathrm{DM}} = 0.262125$, and $h = 0.6766$, with the parameters defined as their usual definitions.

Once the original simulation finished, we restarted the simulation with different NSM parameters. Specifically, we vary the explosion energy of the NSM itself and the delay time, the time between NS binary system formation and NSM. In the next sections, we discuss the NSM model that has been added to Enzo, and the NSM simulation suite.

\subsection{Neutron star merger model and simulation suite} \label{sec:NSM_model}
We implement a new NSM model within \enzo{} to control the delay time and the explosion energy of the event, modelled as a single star particle. Upon completion of the original simulation, a single Pop III star is chosen as the candidate NSM event. The chosen Pop III star must be between $20 \leq M / M_{\odot} \leq 30$ so that when this system is split into a symmetric binary system, the initial masses of the component Pop III stars is between $10 \leq M / M_{\odot} \leq 15$, corresponding to the SN models from \citet{Heger10} which will produce a NS as a remnant. We use their model C as a point of reference since the explosion energy, $0.9 \times 10^{51}$ erg, is the closest to the CCSN explosion energy in Enzo. The simulation is restarted at the output where the Pop III star forms, indicating which Pop III star and what NSM parameters should be included. We chose the first allowed Pop III star that forms in the simulation to become the source of the NSM event in order to allow for the maximum amount of time between the NSM event and for the second generation of stars to form. The Pop III star that we chose has an initial mass of $28.7 M_{\odot}$ that was randomly selected from an IMF described in \ref{IMF}. The chosen Pop III star is then converted into a symmetric Pop III binary system with component masses of $\sim 14.35 M_{\odot}$, but is still modelled as a single star particle with an ionizing hydrogen photon rate of $2.9 \times 10^{48} [\mathrm{s}^{-1}]$, which is equal to the sum of the two individual stellar photon rates from \citet{Schaerer02}.

The Pop III binary system then undergoes its first explosion via a CCSN with an explosion energy of double that of a normal CCSN since we are modelling two stars in one, with a total explosion energy of $2 \times 10^{51}$ erg. The remnant particle is now labelled as a NS binary system. To determine the masses of the remnant NSs, we fit a parabola (\ref{eq:nsm_mass}) to the model C data from Figure 6 in \citet{Heger10}. The coefficients are fit to within 1\% of the standard error. The remnant now has a total mass of $\sim 4.8 M_{\odot}$, with the component masses each having a mass of $\sim 2.4 M_{\odot}$, making this system a higher mass NS binary system.

\begin{equation} \label{eq:nsm_mass}
	M_{\mathrm{NS}} = 0.01319 M_{\mathrm{PopIII}}^{2} - 0.0421 M_{\mathrm{PopIII}} + 0.301
\end{equation}

A second explosion goes off with $E_{\textrm{NSM}}$ after a time $t_{\textrm{merge}}$, with the parameters chosen in a particular run given the choices in Table \ref{tab:NSM_params}. The final remnant particle is then converted to an inert particle with a mass equal to the sum of the remnant masses. We do not consider any EM radiation from the NSs nor any kilonova effects of a NSM for simplicity; we only follow the mass ejected from this event. For this proof of concept, the total ejecta mass is set to $0.01 \Ms$, but in practice, due to the Cartesian discretization of a sphere in of Enzo, the actual mass ejected is $0.0169 M_{\odot}$.

Table \ref{tab:NSM_params} shows the NSM parameters for each run of this simulation suite. Each simulation was restarted when the chosen Pop III star first forms, at $z = 20.1$ and is run until $z = 10$. Before $z = 20.1$, all simulations share the same datasets as the original run. We run \rockstar{} \citep{rockstar} on each run to identify the main halo and the most massive progenitor line.

\begin{table}
	\centering
	\begin{tabular}{lcc} 
		\hline
		 & $t_{\textrm{merge}}$ [Myr] & E$_{\textrm{NSM}}$ [erg] \\
		\hline
		Fiducial & 100 & $10^{50.5}$ \\
		A & \textbf{10} & $10^{50.5}$ \\
		B & \textbf{30} & $10^{50.5}$ \\
		D & 100 & $\mathbf{10^{50}}$ \\
		E & 100 & $\mathbf{10^{51}}$ \\
		No NSM Event & -- & -- \\
		\hline
	\end{tabular}
	\caption{Parameter choices for each simulation. Non-Fiducial parameters are bolded.}
	\label{tab:NSM_params}
\end{table}

\subsection{Pop III and Pop II star formation and feedback} \label{sec:star_formation}
We will briefly discuss the formation of Pop III and Pop II stars in the simulation. For more detailed descriptions, we refer the reader to \citet{Skinner20}. A Pop III star will form when the following criteria are met within a cell: 
\begin{enumerate}
	\item metallicity of $\mathrm{Z} \leq 1.295 \times 10^{-6} \mathrm{Z}_{\odot}$
	\item gas number density of $\mathrm{n} > 10^{6} \mathrm{cm}^{-3}$
	\item converging gas flow: $\nabla \cdot \mathrm{v}_{\mathrm{gas}} < 0$
	\item molecular hydrogen number fraction of $\mathrm{f}_{\mathrm{H}_{2}} > 10^{-3}$
\end{enumerate}
Pop III stars have mass-dependent lifetimes and produce hydrogen ionizing and Lyman-Werner luminosities from \citet{Schaerer02}. Their SN and end states depend on their mass-dependent stellar endpoints. A Pop III particle represents a single Pop III star.

A Pop II star forms using the same criteria, except without the molecular hydrogen fraction requirement, and with a metallicity greater than the above value. A Pop II particle represents a cluster of Pop II stars with a minimum cluster mass of 1000 \Ms. There are instances when a Pop II star will form below the minimum mass, in which case the star accretes mass without producing feedback until it reaches that minimum mass. Both Pop III and Pop II stars are assigned a metallicity based on the metallicity fraction of the cell that the particle forms in. Because Pop II stars form as star clusters, the exact number of Pop II star particles that form is not a good indicator of how productive an environment is at forming Pop II stars. Rather, the total Pop II stellar mass is the indicator that will be presented throughout this work.

%We use the adaptive mesh refinement, hydrodynamical cosmological simulation code \enzo to run high-resolution simulations of a NSM in a progenitor UFD galaxy, and we analyze the simulations with the analysis toolkit \yt. We use the 12-species (H2, H2+, H-. H, H+, He, He+, He++, e-, D, D+, and HD) non-equilibrium chemistry model (CITE: Abel, Zhang, Anninos).

%To simulate a progenitor UFD galaxy, we run a zoom-in simulation of a 4 Mpc$^{3}$ comoving box with a 512$^{3}$ base grid resolution and a DM particle mass of \unk. -- how to describe the nested simulations - this will depend a bit on which one we end up analyzing%
 %
%\subsubsection{Choosing a progenitor UFD}
%Simulating a progenitor UFD requires some strategic decision making that will increase one's chances of ending up with a UFD galaxy at $z = 0$, and due to the sheer number of halos that can be identified within a single simulation, making smart decisions about which halo is chosen is critical. Since we do not run our simulations to present day, we chose our target halo given the constraints from \citet{Safarzadeh18}. In their work, they find that halos chosen at higher redshifts, with lower virial ratios, and at large distances from nearby galaxies are 3 times more likely to end up as an UFD galaxy at $z = 0$. To chose our target halo, we run the halo finding code \rockstar \citet{rockstar} on our unigrid simulation at $z = 8$ to identify all the halos within the simulation, amounting to a total of 31,324 halos. \rockstar identifies haloes in position and velocity phase space and adaptively refines halos using a friends-of-friends method (maybe can move this sentence to the previous section). At this redshift, \citet{Safarzadeh18} recommends choosing a halo with a mass in the range of $10^{7} < M / M_{\odot} < 10^{8}$. Within this mass range, about 10\% of halos survive to $z = 0$ as an UFD galaxy. For our halos, we chose a mass range of $10^{7.57} < M / M_{\odot} < 10^{8.5}$, to incorporate some larger halos into the mix. On our first round of choosing a halo, we chose a halo with a mass of $\approx 10^{7.5} M_{\odot}$, which was not massive enough to maintain it's gas content as stars began to form. Thus, we increased the halo mass range from the recommended mass range. Making this cut of halo masses drops our pool of halos down to 796. Next, we looked at the virial ratio of our halos and chose all the halos with $Log(2T/|U|) < 0.20$, again following the recommendation from \citet{Safarzadeh18} to chose a halo with a low virial ratio. The low virial ratio implies that the halos formed at higher redshifts and have not undergone any recent major merger activity, and thus have been relatively untouched and isolated. Making this cut brings our pool of halos down to 556. Our final criteria comes from choosing a halo that is far away from other massive galaxies. We calculate the distance from each of our potential halos to their sixth nearest neighbor with a mass greater than $10^{7.57} M_{\odot}%$ (DS: why?), and choose only the halos with a nearby distance greater than $10^{2.8} kpc/h$. This ensures that the progenitor halo has a long infall time to the nearby main progenitor. We are finally left with 14 halos to choose from. 
%
% Example figure%
%\begin{figure}
%	\includegraphics[width=\columnwidth]{plots/halo_cuts.pdf}
    %\caption{Pool of potential halo candidates. The left plot shows a 2d histogram of the halo masses and the $Log(2T/|U|)$ for all of the halos within the chosen mass range. The red line indicates the maximum virial ratio we allowed for ($Log(2T/|U|) = 0.20$), and the direction of the arrow shows that all the halos to the left of that line are moved on to the next step, which is shown in the right panel. The right panel shows a 2d histogram of the halo masses and the distance to the sixth nearest massive neighbor for all of the halos to the left of the line in the left panel. The red line indicates our minimum distance we allowed for ($10^{2.8} kpc/h$), and the direction of the arrow shows that all of the halos to the right of that line end up in our final pool of candidates.}
%    \label{fig:UFD_candidates}
%\end{figure}

%To choose from this final set of halos, we looked at each halo's growth history. We used consistent trees \citep{Behroozi13_trees} to calculate the halo merger tree for each halo, and looked at the main progenitor mass as a function of time. Based on our past experience of choosing a halo that ended up blowing out all of it's gas after star formation occurred, we wanted to choose a halo that had a rapid initial growth, to make sure that the halo had a sufficient amount of mass to withstand star formation. We had one halo with a particularly rapid halo growth early on. Our target halo has a DM halo mass of $10^{8.26} M_{\odot}$ and is the sole focus of our zoom-in simulations.

%====================================================================
\section{Results} \label{sec:results}
%====================================================================

We discuss the evolution of the main halo in the original run in \ref{sec:main_halo}. In \ref{sec:energy_vary} and \ref{sec:time_vary}, we describe the explosion energy variation runs and the delay time variation runs.

\subsection{Evolution of the main halo} \label{sec:main_halo}

The most massive progenitor of the main halo is first identified at $z \approx 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$. During that time, the halo forms two Pop III stars with masses of 26.5 \Ms{} and 195.5 \Ms{} at 150.7 Myr ($z = 22.6$) and 286.1 Myr ($z = 14.4$), respectively. The halo experiences 25 Pop III SN from stars that accrete into the halo and from the two that form within the main progenitor of the halo. 26 Pop II star particles form within the halo with a total stellar mass of $10^{4.5} \Ms$, and with a median and mean mass weighted creation time of 441 Myr ($z = 10.5$) and 402 Myr ($z = 11.3$), respectively. There are also five Pop II star particles that fall inside the halo. Figure \ref{fig:og_stellarmass} shows the radial distribution of Pop III and Pop II stars within the halo at $z = 10$. The half-mass radius is 331.2 pc, which is on the higher end of results from other simulations of UFD galaxies \citep{Ricotti16}. The Pop II stars all tend to cluster within 1 kpc of the center of the halo, while the Pop III stars are more dispersed throughout the halo.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/run_OG_stellar_dist.pdf}
	\caption[Radial distribution of Pop II and III stars in the main halo.]{The radial distribution of Pop III and Pop II stars in the halo in the original run at $z = 10$. The orange and blue lines show the Pop III and Pop II stars, respectively. The black line indicates the virial radius of the halo. The half-mass radius for this halo is 331.2 pc}
	\label{fig:og_stellarmass}
\end{figure}

This halo merges with a neighboring smaller halo that has formed its own distribution of Pop III and II stars, which is where a majority of the stars that fell in came from. This results in a mix of stars that reside within the final halo, those that formed within the main progenitor, and those that formed outside. This can be seen in Figure \ref{fig:og_evolution}, where Pop III and Pop II stars form within 5 kpc of the main halo, and end up combining within the final halo at $z = 10$. This feature will be of particular interest in the NSM runs.

\begin{figure*} 
	\includegraphics[width=\textwidth]{plots/OG_evolution.pdf}
	\caption[Projections of the density, temperature and Pop III metallicity of the main halo through time.]{Evolution of the main halo. The left column shows the $z = 19.4$ timestep, when the chosen Pop III star explodes as a hypernova, the middle $z = 15$, and the right $z = 10$. The top row shows the projected gas density, the middle the projected temperature, and the bottom the projected metallicity from Pop III stars. The star particles are only plotted in the bottom row. The white circle indicates the halo virial radius, the yellow dots show the Pop III stars, and the aqua dots show the Pop II stars. The white dot indicates the particle chosen to be the NSM in the other runs.}
	\label{fig:og_evolution}
\end{figure*}

By $z = 10$, the halo has a Pop II stellar mass of $\sim 10^{4.4} \Ms$ and a Pop III stellar mass of $\sim 978 \Ms$. At this time, there are still 14 Pop III stars living within the halo, concurrently with Pop II stars. We stress that the number of Pop II star particles is not of particular importance, since they represent clusters of Pop II stars. The overall mass distribution of Pop II stars is relevant, and thus when discussing the Pop II distribution, we will focus on the Pop II stellar masses.

\subsection{Explosion energy variation runs} \label{sec:energy_vary}

In each of these runs, where the NSM explosion energy is varied in the range $10^{50 - 51}$ erg, the NSM takes place at the same time at $286$ Myr ($z = 14.4$). The general dynamics of the halo remain unchanged, and the main halos in the NSM runs looks visually similar to the halo in the original run. Run D, Fiducial, and E have Pop II stellar masses of $10^{5.27}$, $10^{4.87}$, and $10^{4.80}$ \Ms{}, at $z = 10$ respectively, i.e. the lowest energy run produces the highest Pop II stellar mass. The median and mean mass weighted creation times for the Pop II stars that form within the halo for runs D, Fiducial, and E are 462 Myr ($z = 10.2$) and 455 Myr ($z = 10.3$), 456 Myr ($z = 10.3$) and 443 Myr ($z = 10.5$), and 443 ($z = 10.5$) Myr and 436 Myr ($z = 10.6$) respectively. The mean creation time for Pop II stars in these runs is higher than the mean creation time in the original run. Runs D and Fiducial form 2 Pop III stars at 151 Myr ($z = 22.6$) and 353 Myr ($z = 12.4$) and at 151 Myr ($z = 22.6$) and 266 Myr ($z = 15.2$), with masses of 26.5 \Ms{} and 27.7 \Ms{}, and 26.5 \Ms{} and 30.4 \Ms, respectively. Run E produces only one Pop III star at 151 Myr ($z = 22.6$) with a mass of 26.5 \Ms{}. The halos in runs D, Fiducial and E experience 39, 38, and 33 Pop III SNe and contain 22, 23, and 19 living Pop III stars at $z = 10$.

We show the halo mass, Pop II stellar mass, gas fraction, and r-process mass of the most massive halo progenitor in Figure \ref{fig:eng_evol}. Halo masses in each run are almost identical to each other, and with runs D, Fiducial, and E growing to $10^{8.3} \Ms$ and the original run to $10^{8.2} \Ms$. The Pop II stellar mass follows a relatively similar trend in each run, but the NSM runs end with larger Pop II stellar masses as compared to the original run. The lowest energy run forms the most, followed by the middle energy, and finally the highest energy run. This is consistent with what is expected of an explosion within a halo. The higher the explosion energy, the more vulnerable the halo will be to disruption from the event. The gas fraction dips at around 200 Myr in each run due to the formation of the first stars within the halo, which is quite small at this point in time. This star formation event blows out most of the gas through radiative and SN feedback. As halo mergers takes place, the gas fraction recovers and steadily rises to $\sim 0.1$. The bottom panel of Figure \ref{fig:eng_evol} shows the r-process mass ejected from the NSM within the halo as a function of time. When the NSM occurs, the entirety of the explosion is contained within each halo. The lowest energy run experiences an abrupt dip in the r-process mass due to some of the mass being blown out by SN that occur outside and within the halo. This mass is eventually gravitationally pulled back into the halo as merging occurs. The r-process mass in each run slowly decreases as star formation takes place and some of the r-process material is deposited into star particles.

The evolution of the r-process metallicity field can be seen in Figure \ref{fig:eng_met4_evol}. The first column shows the timestep where the NSM takes place. At this time, the highest energy run expands more quickly into the halo, as expected. Later at $z = 12$, the Fiducial run (middle energy) is still fully contained within the halo, while the lowest and highest energy runs are starting to escape. This is caused by a SN that occurred just outside the halo and within the halo right around $z = 12$ in the lowest and higher energy runs. This blows some of the r-process enhanced gas out of the halo in these runs. By the end of the simulation at $z = 10$, any r-process enhanced gas that was lost due to stellar feedback has mostly returned to the halo. This is also evident in the bottom panel of Figure \ref{fig:eng_evol}, where the r-process mass in the lowest energy run dips at around $\sim 325$ Myr, but recovers quickly as that gas gravitates back inwards. This effect is most prominent in the lower energy run. All runs have a slight decrease in the r-process mass with time and as star formation occurs and consumes it.

To better represent the r-process metallicity, we define a new unit $Z_{\mathrm{r}} = 1.6 \times 10^{-10}$ which is scaled to the r-process abundances of the solar system from \citet{Goriely99}, normalized by the solar system H abundance. This means that a metallicity of 1 $Z_{\mathrm{r}}$ is equal to the r-process abundances within the solar system.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original run. The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.}
	\label{fig:eng_evol}
\end{figure}

\begin{figure*} 
	\includegraphics[width=\textwidth]{plots/eng_NSM_evolution.pdf}
	\caption[R-process metallicity projections of the explosion energy variation runs through time.]{Evolution of the density-weighted projections of the r-process metallicity for each explosion energy variation run. The first column shows the system at $z = 14.4$, when the NSM event takes place, the middle column shows $z = 12$, and the right column shows the final output at $z = 10$. The top row shows run D, the middle shows the Fiducial run, and the bottom shows run E. The white circle indicates the virial radius of the halo. The yellow dots show Pop III stars, and the aqua dots show Pop II stars. The white dot indicates the chosen Pop III star that produced the NSM event. Note that the star particles are covering the NSM explosion in the lowest and Fiducial runs at the first timestep.}
	\label{fig:eng_met4_evol}
\end{figure*}

The energy variation runs lead to a significantly higher Pop II stellar masses as compared to the original run. Table \ref{tab:eng_stellar} shows the number of Pop III stars and the total Pop II stellar mass in the first two columns. A group of Pop II stars form and cluster within the dense central region of the halo where the NSM takes place, in each run. Figure \ref{fig:eng_stellar_dist} shows the fraction of Pop II stars within some radius for each run. The dotted lines show the half-mass radius, which is much smaller for the NSM runs, with half-mass radii of 37.1 pc, 65.3 pc, and 50.6 pc for runs D, Fiducial, and E. Compared to the original run whose half-mass radius is 331.2 pc, there is a much larger fraction of Pop II stars that have clustered in the central 0.2 kpc, leading to the lower half-mass radii. These smaller half-mass radii are more aligned with results from \citet{Ricotti16}. The NSM runs have higher fractions of cold ($< 10^{3} K$) gas mass at later times, leading to this increase in Pop II star formation.

\begin{table}
	\centering
	\begin{tabular}{lcccc} 
		\hline
		 & \# Pop III & M$_{\mathrm{Tot, P2}} [\Ms]$ & $f_{\mathrm{r}}$ & $f_{\mathrm{r, high}}$ \\
		\hline
		Fiducial & 2 & $10^{4.87}$ & 80\% & 80\% \\
		D & 2 & $10^{5.27}$ & 91\% & 63\% \\
		E & 1 & $10^{4.80}$ & 74\% & 74\% \\
		Original & 2 & $10^{4.52}$ & -- & -- \\
		\hline
	\end{tabular}
	\caption[Information about the stellar populations within the explosion energy variation runs.]{Information about the stellar populations within the explosion energy variation runs. For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-8} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
	\label{tab:eng_stellar}
\end{table}

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_stellar_dist.pdf}
	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original run. The dashed lines indicate the half-mass radius, which are 331.2 pc, 37.1 pc, 65.3 pc, and 50.6 pc for the original run, run D, run Fiducial, and run E, respectively. The virial radius at this time is 1.6 kpc, 1.73 kpc, 1.72 kpc, and 1.73 kpc for the original run, run D, run Fiducial, and run E, respectively.}
	\label{fig:eng_stellar_dist}
\end{figure}

As the main halo assembles, and the neighboring halo falls in with its own pool of Pop II stars, the final halo ends with a mix of r-process enhanced and non-enhanced Pop II stars. This can be clearly seen in Figure \ref{fig:eng_NSM_p3}, where we are showing the NSM r-process metallicity fraction versus the total metallicity fraction, defined as the Pop III plus the Pop II metallicity fraction, of Pop II stars at $z = 10$. There is a collection of Pop II stars that are enriched with r-process material, and a separate group, at very low r-process metallicity fractions that formed either before the NSM occurred, or outside the enrichment zone. As Pop II stars form at later times, their r-process metallicity fractions decrease slightly, along with their total metallicity fraction. There is also a group of Pop II stars that form at very late times with high r-process metallicity fractions but low total metallicity fractions.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_NSM_tot.pdf}
	\caption[R-process metallicity fraction versus the total metallicity fraction for Pop II stars in the explosion energy variation runs.]{The r-process metallicity fraction versus the total metallicity fraction of Pop II stars at the final redshift. The different marker types are distinguished in the legend. The points are colored by their creation time. Note that the NSM occurs in these runs at $\sim 286$ Myr. We have also artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$ for clarity.}
	\label{fig:eng_NSM_p3}
\end{figure}

Figure \ref{fig:eng_NSM_deltat} shows the r-process metallicity of the Pop II stars that formed within the halo as a function of their creation time relative to the NSM event. We define stars to be ``highly r-process enhanced'' if they have a metallicity of $> 10^{-1} Z_{\mathrm{r}}$ and to be ``r-process enhanced'' if they have a metallicity of $> 10^{-8} Z_{\mathrm{r}}$. At $z = 10$, we find that runs D, Fiducial and E have Pop II mass fractions of 80\%, 91\% and 74\% being r-process enhanced, and Pop II mass fractions of 80\%, 63\%, and 74\% being highly r-process enhanced, respectively. The lowest explosion energy results in a lower percentage of highly r-process enhanced stars, but the highest percentage of r-process enhanced stars overall. As the energy increases, all Pop II stars that are enriched by the NSM are highly enhanced. This is due to the large amount of Pop II stars that form at late times near the center of the halo, where the majority of the r-process enhanced gas is contained. Figure \ref{fig:eng_NSM_deltat} also indicates that the Pop II stars that form closer to the NSM tend to have higher r-process metallicity fractions than if they were to form later on. We also see that the higher explosion energies produce Pop II stars with higher r-process metallicities, but less Pop II stars overall.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_NSM_deltat.pdf}
	\caption[R-process metallicity as a function of $\Delta t_{\mathrm{NSM}}$ for the energy variation runs.]{The r-process metallicity for Pop II stars that formed in the halo as a function of when they formed relative to the NSM. The blue stars indicate Pop II stars formed in run D, the orange diamonds from run Fiducial, and the green squares from run E. We have artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$ for clarity.}
	\label{fig:eng_NSM_deltat}
\end{figure}

\subsection{Delay time variation runs} \label{sec:time_vary}

Runs A, B and Fiducial vary the delay time of the NSM by 10, 30 and 100 Myr, respectively. The NSM occurs in runs A, B and Fiducial at 197 Myr ($z = 18.7$), 216 Myr ($z = 17.6$) and 286 Myr ($z = 14.4$), respectively. Similar to the energy variation runs, the dynamics and visual appearance of the halos remains similar to the original run. Run A ends with a total Pop II stellar mass of $10^{5.25} \Ms$, with the mean and median creation time of Pop II stars being 455 Myr ($z = 10.3$) and 465 Myr ($z = 10.1$). A total of 6 Pop III stars form within the main halo progenitor of run A, with three forming at 474 Myr ($z = 10.0$) with masses of 43.3 \Ms{}, 27.7\Ms{}, and 12.5 \Ms{}, one at 369 Myr ($z = 12.0$) with a mass of 56.9 \Ms, one at 358 Myr ($z = 12.3$) with a mass of 20.4 \Ms{}, and the first forming at 151 Myr ($z = 22.6$) with a mass of 26.5 \Ms. All halo progenitors experience 29 Pop III SNe. By $z = 10$, there are still 21 Pop III stars living within the halo. Run B ends with a total Pop II stellar mass of $10^{5.8} \Ms$, with the mean and median mass weighted creation time of Pop II stars being 455 Myr ($z = 10.3$) and 458 Myr ($z = 10.2$). Three Pop III stars form within the main halo progenitor of run B, at 473 Myr ($z = 10.0$), 343 Myr ($z = 12.6$), and 151 Myr ($z = 22.6$) with masses of 17.9 \Ms{}, 152.7 \Ms{}, and 26.5 \Ms{}, respectively. All halo progenitors experience 32 Pop III SNe, and by $z = 10$, there are still 24 Pop III stars still living within the halo. We refer the reader to the top of the previous section for a reminder of these values for the Fiducial run.

Figure \ref{fig:time_evol} shows the halo mass, the Pop II stellar mass, the gas fraction and the r-process mass as a function of time. The halo mass for these runs, like the explosion energy variation runs, are almost identical to each other, with the halos growing to $10^{8.3}$ \Ms{} for runs A and B. The Pop II stellar mass steadily increases as time increases, with run B ending with the highest Pop II stellar mass, followed by run A, then the Fiducial run, and finally the original run. The gas fraction in each run also follows a similar trend, with the first dip in gas fraction occurring due to the formation of the first stars when the halo was quite small, at $10^{6.6} \Ms$ for the original run and run A, and $10^{6.7} \Ms$ for runs B and Fiducial. The gas fraction steadily recovers, with the 30 Myr run overtaking the others with a higher gas fraction by 314 Myr. The bottom panel shows the r-process mass within the halo as a function of time, and the different runs have very different structures. The NSM in run A, when the delay time is 10 Myr, occurs very early when the halo was very small at a mass of $10^{6.4} \Ms$. The NSM ejects the r-process material out of the halo right away, which is why the initial r-process mass is smaller than the amount that is actually injected. In run B, when the delay time is 30 Myr, the r-process mass is mostly contained within the halo when the mass was $10^{6.7} \Ms$ at the time of the NSM but quickly starts to spread outward, past the bounds of the virial radius. A Pop III SN that occurs just on the boundary of the halo then carries this material even further outside the halo, resulting in the decrease in the r-process mass around 270 Myr. As merging takes place, some of this material is recovered, but an r-process ``tail'' remains outside of the halo.

The evolution of the r-process metallicity field can be seen in Figure \ref{fig:time_met4_evol}. The top row represents run A, the middle run B, and the bottom the Fiducial run. The first column shows the timestep when the NSM takes place, which occurs at different times for these runs, based on their delay time. The middle column shows $z = 12$, and the right column shows the final redshift at $z = 10$. When the NSM occurs in run A, because the halo is so small at this early time, the r-process material is not contained within the halo, but extends outside of the halo. By $z = 12$, there are a number of Pop III stars that go SN and Pop II stars that form just outside of the halo, all of which pushes the gas outside of the halo even further through external feedback. As time progresses, some of the r-process material is recovered, but a large tail, or wing like structure remains outside of the halo. Run B follows a similar story as run A, with a similar structure appearing at $z = 10$. The total r-process mass is similar for these two runs by the end of the simulation. These short delay times appear very different as compared to the longer delay time, where the r-process material is always fully contained within the halo.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/time_evolution.pdf}
	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for each delay time variation run.]{The evolution of the main halo in each delay time variation run and the original run. The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.}
	\label{fig:time_evol}
\end{figure}

\begin{figure*} 
	\includegraphics[width=\textwidth]{plots/time_NSM_evolution.pdf}
	\caption[Projections of the r-process metallicity field for each delay time variation run through time.]{The r-process metallicity evolution for each delay time variation run. The first column shows the timestep at $z = 18, 17.5$ and $14.4$, when the NSM event takes place, the middle column shows $z = 12$, and the right column shows the final timestep of $z = 10$. The top row shows run A, the middle shows run B, and the bottom shows the Fiducial run. The white circle indicates the virial radius of the halo. The yellow dots show Pop III stars, and the aqua dots show Pop II stars. The white star indicates the chosen Pop III star that produced the NSM event. Note that the star particles are covering the NSM explosion in the Fiducial run at the first timestep.}
	\label{fig:time_met4_evol}
\end{figure*}

Similar to the energy variation runs, the time delay runs lead to significantly higher Pop II stellar masses as compared to the original run. Runs A, B, and Fiducial end with Pop II stellar masses of $10^{5.25}\Ms$, $10^{5.58} \Ms$, and $10^{4.87}$ \Ms. Run A also produces 6 Pop III stars within the main halo progenitor, which is the highest number of Pop III stars formed within the main halo of all the runs. Table \ref{tab:time_stellar} presents this information in the first two columns. Figure \ref{fig:time_stellar_dist} shows the fraction of Pop II stars that exist within a certain radius for each run. The half-mass radius is indicated as the dotted line for each run and is 59.2 pc, 53.3 pc, and 65.3 pc for runs A, B, and Fiducial. There is a large cluster of Pop II stars that gathers near the center of the halo for each of the NSM runs, resulting in smaller half-mass radii. As with the energy variation runs, these half-mass radii are similar to those that have been found previously in simulations of UFD galaxies \citep{Ricotti16}. This larger group of Pop II stars originates from the NSM runs having higher cold gas mass fractions at late times as compared to the original runs.

\begin{table}
	\centering
	\begin{tabular}{lcccc} 
		\hline
		 & \# Pop III & M$_{\mathrm{Tot, P2}} [\Ms]$ & $f_{\mathrm{r}}$ & $f_{\mathrm{r, high}}$ \\
		\hline
		Fiducial & 2 & $10^{4.87}$ & 80\% & 80\% \\
		A & 6 & $10^{5.25}$ & 79\% & 50\% \\
		B & 3 & $10^{5.58}$ & 80\% & 24\% \\
		Original & 2 & $10^{4.52}$ & -- & -- \\
		\hline
	\end{tabular}
	\caption[Information about the stellar populations within the delay time variation runs.]{Information about the stellar populations within the delay time variation runs. For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-8} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
	\label{tab:time_stellar}
\end{table}

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/time_stellar_dist.pdf}
	\caption[Radial distribution of Pop II stars in the delay time variation runs.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs A, B and Fiducial, and the original run. The dashed lines indicate the half-mass radius, which is 331.2 pc, 59.2 pc, 53.3 pc, and 65.3 pc for the original run, run A, run B, and run Fiducial respectively. Note that the virial radius at this time is 1.6, 1.72, 1.72, and 1.73 kpc for the original run, run A, run B, and run Fiducial, respectively.}
	\label{fig:time_stellar_dist}
\end{figure}

Figure \ref{fig:time_NSM_p3} shows the r-process metallicity fraction versus the total metallicity fraction for the Pop II stars at $z = 10$. Unlike the energy variation runs, there is slightly more scatter in the NSM metallicity fraction. There is a large portion of Pop II stars that form at low total metallicities but at relatively higher r-processed metallicities. This is again due to Pop II stars forming near the center of the halo where there is still a strong nucleus of r-process material.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/time_NSM_tot.pdf}
	\caption[R-process metallicity fraction versus total metallicity fraction of Pop II stars in the delay time variation runs.]{The r-process metallicity fraction versus the total metallicity fraction of Pop II stars at the final redshift. The different marker types are distinguished in the legend. The points are colored by their creation time. Note that the NSM occurs in runs A, B, and Fiducial at 197 Myr, 216 Myr, and 286 Myr, respectively. We have also artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$.}
	\label{fig:time_NSM_p3}
\end{figure}

Figure \ref{fig:time_NSM_deltat} shows the r-process metallicity for Pop II stars as a function of their creation time relative to when the NSM occurred. In this plot, there are obvious groups of stars that come from the different runs. Run A, with the shortest delay time, forms Pop II stars at later times compared to when the NSM occurs, and at both high and low r-process metallicities. Run B, with the 30 Myr delay time, forms the highest amount of Pop II stars, but with relatively lower r-process metallicities overall. The Fiducial run forms Pop II stars the soonest after the NSM, which occurs simply because the delay time is longer, and with higher r-process metallicities. In this run, there hasn't been enough time for the material to escape the halo before Pop II Stars form, therefore, higher r-process metallicities are expected. We find that run A results in a 79\% and 50\% of the Pop II mass fraction being r-process enhanced and highly r-process enhanced, run B resulting in 80\% and 24\%, and run Fiducial resulting in 80\% and 80\% of the Pop II stars being r-process enhanced and highly r-process enhanced, respectively. This indicates that the NSM is in general enhancing a similar percentage of Pop II stars with r-process material, but the shorter delay times result in a smaller percentage of Pop II stars being highly r-process enhanced.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/time_NSM_deltat.pdf}
	\caption[R-process metallicity fraction as a function of $\Delta t_{\mathrm{NSM}}$ for the delay time variation runs.]{The r-process metallicity for Pop II stars that formed in the halo as a function of when they formed relative to the NSM. The blue stars indicate Pop II stars formed in run A, the orange diamonds from run B, and the green squares from run Fiducial. We have artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$ for clarity.}
	\label{fig:time_NSM_deltat}
\end{figure}

%====================================================================
\section{Discussion} \label{sec:discussion}
%====================================================================

This work represents some of the first simulations on the chemical and dynamical impacts of a NSM, with various parameters, in a cosmological setting, and thus there are some difficulties that come with this kind of study. The first is that the small sample size prevents us from saying anything conclusive about the NSM parameters in general. While we see some trends across the data, the inherent randomness across simulations leads to different amounts of star formation at different times and locations. On top of that, because we randomly sample the Pop III IMF, if two simulations are looking very similar and both go on to form a Pop III star in a similar location, one can be sampled at a low mass and the other at a very high mass, and affect the surrounding region in completely different ways. What may seem like a small difference in the Pop III stellar mass can go on to have impactful consequences on future star formation. This means that it can be difficult to pick apart why certain stars form where and at what times. We stress that this is merely a proof-of-concept study to show that we can study the impacts of NSMs in a cosmological setting to present meaningful results that can enhance our understanding of r-process enrichment in the early universe.

The NSM model we implement here is relatively simple in order to understand the impacts of only a small amount of parameters. We manually choose which Pop III star to become the Pop III binary system, and thus the NSM, and follow only a general r-process metal field to $z = 10$. The simple model allows us to focus on just the r-process enrichment of the halo in order to better understand how this simple model behaves and how the r-process field affects the second generation of stars. But because it is relatively simple, we lack the full details of NSMs in the universe. Some details that could be included would be to automatically form a NSM given some NSM rate, to include asymmetric NSMs and kilonova effects, and to follow individual metal species. These are all next steps to what is a long endeavor in this field of simulating NSMs in a cosmological setting.

Finally, if we want to get a better sample size of how NSMs affect the second generation of stars, many simulations would need to be run, or a single larger simulation would need to be executed, in which case the resolution that can be achieved in zoom-in simulations are lost. Simulations are in general not cheap to run, but to better understand the impacts of these parameters on star formation, a larger sample size is needed. Implementing an automatic NSM model within cosmological simulations that assigns various explosion energies and delay times would better help us constrain the impacts of these events on metal-enriched star formation in the early universe.

%====================================================================
\section{Conclusions} \label{sec:conclusion}
%====================================================================

We have run a suite of simulations studying the impact of Pop III remnants, in the form of NSMs, on the second generation of star formation in the universe. We ran one simulation without a NSM, and five simulations varying the explosion energy and the delay time of the NSM in order to see how these variations affect the r-process abundances of the next generation of stars. In our case study, we find that:
\begin{itemize}
	\item NSMs do lead to a substantial fraction of highly r-process enhanced Pop II stars.
	\item When the explosion energy is high, 74\% of stars are highly r-process enhanced, versus when the explosion energy is lower, only 63\% are highly r-process enhanced. 
	\item The lower explosion energy leads to a higher fraction of Pop II stars being r-process enhanced overall, but at lower metallicities in general. The higher explosion energy leads to a smaller fraction of r-process enhanced stars, but all that are enhanced are highly enhanced. 
	\item The longer time delays lead to higher mass fractions of highly r-process enhanced stars, due to the NSM occurring closer to the period of Pop II star formation. 
	\item The shorter time delays still lead to a high mass fraction of r-process enhanced stars, but a smaller fraction of highly r-process enhanced stars.
	\item The half-mass radius significantly decreases in each NSM run due to the large number of Pop II stars that form and cluster near the center of the halo. 
	\item Star formation and feedback that occurs in and around the halo heavily governs the dynamics and details of star formation in these runs. A larger sample size of galaxies with NSMs is needed in order to more fully understand the impact of a NSM on the second generation of stars. 
\end{itemize}

Given that we have shown that this simple NSM works well to study how a NSM might affect star formation in the early universe, our next steps are to run the model on a simulation of an UFD progenitor halo in order to attempt to recreate Ret II. These simulations are ongoing and will be an extension of this work. After that, improving the NSM model and following individual metal species, as discussed in Section \ref{sec:discussion} would greatly enhance the detail of this work. This work shows that NSMs can lead to significant amounts of r-process enrichment in Pop II stars, and will aid our understanding of the source of r-process materials in the universe and the nature of Pop III stars.

\section*{Acknowledgements}

DS is supported by the NASA FINESST fellowship award 80NSSC20K1540. The figures in this paper were constructed with the plotting library \textsc{matplotlib} \citep{matplotlib}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\typeout{}
\bibliography{drenniks} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%\appendix

%\section{Some extra material}

%If you want to present additional material which would interrupt the flow of the main paper,
%it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2023-07-11 NSM_mixing.tex
Adding acknowledgements
Making edits in response to John's comments.

@@
 % Keep the title short and informative.
-\title[NSM Impact]{Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe}
+\title[NSMs from Pop III stars]{Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. Skinner et al.]{
+\author[Skinner \& Wise]{
 Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
@@
 The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants.
-The compact objects can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to take place.
+These compact objects can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to take place.
 In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution in order to understand the impact on the second generation of stars and their metal abundances.
@@
 A high explosion energy leads to all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced.
-When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller fraction being highly r-process enhanced.
+When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly r-process enhanced.
 This work represents a stepping stone towards understanding how these events impact their environments and metal abundances of descendant generations of stars.
@@
 During this process, in regions of very high neutron densities, when the rapid bombardment of neutrons onto nuclei is faster than the rate of beta decay, nuclei can build up to produce heavy, stable elements, like Eu, Os, Ir, Pt, Th, and U.
-But the exact origin of this process hasn't been completely pinned down yet \citep{Cowan21, Kajino19}.
+But the exact origin of this process hasn't been completely pinned down yet \citep{Kajino19, Cowan21}.
 
 The r-process likely takes place in events that are either related to massive stars or through compact binary mergers.
-SNe of massive stars can produce r-process elements (see \citet{Cowan21} for a discussion on different sources).
+SNe of massive stars can produce r-process elements \citep[see][for a discussion on different sources]{Cowan21}.
 Core collapse SNe (CCSN) explosions ignited by the magnetorotational explosion model produce r-process elements in both the weak and the strong magnetic field models, with preference given to the strong magnetic field models to explain some r-process abundances of metal-poor stars \citep{Nishimura15}.
@@
 \citet{Goriely11} used relativistic smoothed particle hydrodynamics simulations to study the ejecta of a NSM scenario.
-They model the merging of an equal mass NS system, $1.35 - 1.35 \Ms$, and an asymmetric system, $1.2 - 1.5 \Ms$ and use two different EoSs, one representing a ``soft'' EoS and the other a ``stiff'' EoS.
+They model the merging of an equal mass NS system, $1.35:1.35 \Ms$, and an asymmetric system, $1.2:1.5 \Ms$ and use two different EoSs, one representing a ``soft'' EoS and the other a ``stiff'' EoS.
 A total mass yield of $\sim 10^{-3} - 10^{-2} \Ms$ is ejected in these scenarios, with the asymmetric model ejecting more material than the symmetric model.
@@
 
-The motivation for this work comes from the r-process enriched stars in Ret II.
-Ret II is an UFD galaxy which serves as an ideal laboratory for studying early universe star formation.
+The motivation for this work comes from the r-process enriched stars in Ret II, an ultrafaint dwarf (UFD) galaxy which serves as an ideal laboratory for studying early universe star formation.
 These systems typically form most of their stars early in the universe, before reionization was able to suppress star formation \citep{Weisz14}.
-This means that these stars form in the first couple hundred million years after the Big Bang, and haven't been affected by recent mergers or enriched by recent star formation.
+This means that these stars form in the first couple hundred million years after the Big Bang and haven't been affected by recent mergers or enriched by recent star formation.
 Ret II was detected by the Dark Energy Survey \citep{Bechtol15}, whose stars have since been extensively studied \citep{Simon15, Roederer16, Ji16, Ji22}.
@@
 
-This paper represents the proof of concept for a new NSM model that we have incorporated into Enzo, an adaptive mesh refinement cosmological simulation code.
+This paper represents the proof of concept for a new NSM model that we have incorporated into \enzo{}, an adaptive mesh refinement (AMR) cosmological simulation code.
 We run high-resolution cosmological simulations of a minihalo from a redshift of $z = 250$ to $z = 10$, varying the explosion energy and delay time of a NSM.
 We follow the material ejected into the local environment from this event into the next generation of stars to understand how this material is mixed within the environment and affects the next population of stars.
-The paper is structured as follows: the methods of the simulation is discussion in \ref{sec:methods}, with the added NSM model and the simulation suite described in section \ref{sec:NSM_model}.
-Results are presented in \ref{sec:results}, followed by a discussion in \ref{sec:discussion}.
-We conclude with \ref{sec:conclusion}.
+The paper is structured as follows: the methods of the simulation is discussion in \S \ref{sec:methods}, with the added NSM model and the simulation suite described in \S \ref{sec:NSM_model}.
+Results are presented in \S \ref{sec:results}, followed by a discussion in \S \ref{sec:discussion}.
+We conclude with \S \ref{sec:conclusion}.
 
@@
 
-We use the adaptive mesh refinement, hydrodynamical cosmological simulation code \enzo{} \citep{Enzo} to run high-resolution proof-of-concept simulations of a NSM within a zoom-in simulation of a single progenitor halo, and we analyze the simulations with the analysis toolkit \yt{} \citep{yt_full_paper}.
+We use the AMR, hydrodynamical simulation code \enzo{} \citep{Enzo} to run high-resolution proof-of-concept cosmological simulations of a NSM within a zoom-in simulation of a single progenitor halo, and we analyze the simulations with the analysis toolkit \yt{} \citep{yt_full_paper}.
 We run a total of six simulations, five with a NSM model and one without.
@@
 The original simulation has a domain width of 1 comoving Mpc and a root grid of $64^{3}$ cells.
-We use the 12-species (H2, H2+, H-, H, H+, He, He+, He++, e-, D, D+, and HD) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
+We use the 12-species (H$_{2}$, H$_{2}^{+}$, H$^{-}$, H, H$^{+}$, He, He$^{+}$, He$^{++}$, e$^{-}$, D, D$^{+}$, and HD) non-equilibrium chemistry model \citep{Abel97, Anninos97}.
+We consider metal cooling and use the chemistry and cooling library \grackle{} \citep{grackle}.
 We run this simulation to $z = 10$ and then choose the most massive halo in the box to be the target of a zoom-in simulation.
@@
 Specifically, we vary the explosion energy of the NSM itself and the delay time, the time between NS binary system formation and NSM.
-In the next sections, we discuss the NSM model that has been added to Enzo, and the NSM simulation suite.
+In the next subsections, we discuss the NSM model that has been added to \enzo{}, and the NSM simulation suite.
 
@@
 The chosen Pop III star must be between $20 \leq M / M_{\odot} \leq 30$ so that when this system is split into a symmetric binary system, the initial masses of the component Pop III stars is between $10 \leq M / M_{\odot} \leq 15$, corresponding to the SN models from \citet{Heger10} which will produce a NS as a remnant.
-We use their model C as a point of reference since the explosion energy, $0.9 \times 10^{51}$ erg, is the closest to the CCSN explosion energy in Enzo.
+We use their model C as a point of reference since the explosion energy, $0.9 \times 10^{51}$ erg, is the closest to the CCSN explosion energy in \enzo{}.
 The simulation is restarted at the output where the Pop III star forms, indicating which Pop III star and what NSM parameters should be included.
 We chose the first allowed Pop III star that forms in the simulation to become the source of the NSM event in order to allow for the maximum amount of time between the NSM event and for the second generation of stars to form.
-The Pop III star that we chose has an initial mass of $28.7 M_{\odot}$ that was randomly selected from an IMF described in \ref{IMF}.
+The Pop III star that we chose has an initial mass of $28.7 M_{\odot}$ that was randomly selected from an IMF described in \citet{Skinner20}.
 The chosen Pop III star is then converted into a symmetric Pop III binary system with component masses of $\sim 14.35 M_{\odot}$, but is still modelled as a single star particle with an ionizing hydrogen photon rate of $2.9 \times 10^{48} [\mathrm{s}^{-1}]$, which is equal to the sum of the two individual stellar photon rates from \citet{Schaerer02}.
 
-The Pop III binary system then undergoes its first explosion via a CCSN with an explosion energy of double that of a normal CCSN since we are modelling two stars in one, with a total explosion energy of $2 \times 10^{51}$ erg.
+The Pop III binary system then undergoes its first explosion via a CCSN with an explosion energy of double that of a normal CCSN since we are modelling two stars in one star particle, with a total explosion energy of $2 \times 10^{51}$ erg.
 The remnant particle is now labelled as a NS binary system.
-To determine the masses of the remnant NSs, we fit a parabola (\ref{eq:nsm_mass}) to the model C data from Figure 6 in \citet{Heger10}.
+To determine the masses of the remnant NSs, we fit a parabola (Equation \ref{eq:nsm_mass}) to the model C data from Figure 6 in \citet{Heger10}.
 The coefficients are fit to within 1\% of the standard error.
@@
 We do not consider any EM radiation from the NSs nor any kilonova effects of a NSM for simplicity; we only follow the mass ejected from this event.
+We track the r-process material in a passive scalar field which does not affect metal cooling rates.
 For this proof of concept, the total ejecta mass is set to $0.01 \Ms$, but in practice, due to the Cartesian discretization of a sphere in of Enzo, the actual mass ejected is $0.0169 M_{\odot}$.
@@
 Before $z = 20.1$, all simulations share the same datasets as the original run.
-We run \rockstar{} \citep{rockstar} on each run to identify the main halo and the most massive progenitor line.
+We run \rockstar{} \citep{rockstar} on each run to identify the main halo and use \ytree{} \citep{ytree} to determine the most massive progenitor line.
 
@@
 		\hline
-		 & $t_{\textrm{merge}}$ [Myr] & E$_{\textrm{NSM}}$ [erg] \\
+		Simulation & $t_{\textrm{merge}}$ [Myr] & E$_{\textrm{NSM}}$ [erg] \\
 		\hline
-		Fiducial & 100 & $10^{50.5}$ \\
+		Fiducial (C) & 100 & $10^{50.5}$ \\
 		A & \textbf{10} & $10^{50.5}$ \\
@@
 Their SN and end states depend on their mass-dependent stellar endpoints.
-A Pop III particle represents a single Pop III star.
+A Pop III particle that does not undergo a NSM represents a single Pop III star.
 
@@
 
-We discuss the evolution of the main halo in the original run in \ref{sec:main_halo}.
-In \ref{sec:energy_vary} and \ref{sec:time_vary}, we describe the explosion energy variation runs and the delay time variation runs.
+We discuss the evolution of the main halo in the original run in \S \ref{sec:main_halo}.
+In \S \ref{sec:energy_vary} and \S \ref{sec:time_vary}, we describe the explosion energy variation runs and the delay time variation runs.
 
 \subsection{Evolution of the main halo} \label{sec:main_halo}
-
-The most massive progenitor of the main halo is first identified at $z \approx 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
-During that time, the halo forms two Pop III stars with masses of 26.5 \Ms{} and 195.5 \Ms{} at 150.7 Myr ($z = 22.6$) and 286.1 Myr ($z = 14.4$), respectively.
-The halo experiences 25 Pop III SN from stars that accrete into the halo and from the two that form within the main progenitor of the halo.
-26 Pop II star particles form within the halo with a total stellar mass of $10^{4.5} \Ms$, and with a median and mean mass weighted creation time of 441 Myr ($z = 10.5$) and 402 Myr ($z = 11.3$), respectively.
-There are also five Pop II star particles that fall inside the halo.
-Figure \ref{fig:og_stellarmass} shows the radial distribution of Pop III and Pop II stars within the halo at $z = 10$.
-The half-mass radius is 331.2 pc, which is on the higher end of results from other simulations of UFD galaxies \citep{Ricotti16}.
-The Pop II stars all tend to cluster within 1 kpc of the center of the halo, while the Pop III stars are more dispersed throughout the halo.
-
 \begin{figure} 
@@
 
-This halo merges with a neighboring smaller halo that has formed its own distribution of Pop III and II stars, which is where a majority of the stars that fell in came from.
-This results in a mix of stars that reside within the final halo, those that formed within the main progenitor, and those that formed outside.
-This can be seen in Figure \ref{fig:og_evolution}, where Pop III and Pop II stars form within 5 kpc of the main halo, and end up combining within the final halo at $z = 10$.
-This feature will be of particular interest in the NSM runs.
-
 \begin{figure*} 
@@
 The left column shows the $z = 19.4$ timestep, when the chosen Pop III star explodes as a hypernova, the middle $z = 15$, and the right $z = 10$.
-The top row shows the projected gas density, the middle the projected temperature, and the bottom the projected metallicity from Pop III stars.
+From top to bottom, the rows show the density-weighted projections of gas density, temperature, and metallicity from Pop III stars.
 The star particles are only plotted in the bottom row.
@@
 
-By $z = 10$, the halo has a Pop II stellar mass of $\sim 10^{4.4} \Ms$ and a Pop III stellar mass of $\sim 978 \Ms$.
+The most massive progenitor of the main halo is first identified at $z = 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
+During that time, the halo forms two Pop III stars with masses of 26.5 \Ms{} and 195.5 \Ms{} at 150.7 Myr ($z = 22.6$) and 286.1 Myr ($z = 14.4$), respectively.
+The halo experiences 25 Pop III SN from stars that accrete into the halo and from the two that form within the main progenitor of the halo.
+26 Pop II star particles form within the halo with a total stellar mass of $10^{4.5} \Ms$, and with a median and mean mass weighted creation time of 441 Myr ($z = 10.5$) and 402 Myr ($z = 11.3$), respectively.
+There are also five Pop II star particles that fall inside the halo.
+Figure \ref{fig:og_stellarmass} shows the radial distribution of Pop III and Pop II stars within the halo at $z = 10$.
+The half-mass radius is 331.2 pc, which is on the higher end of results from other simulations of UFD galaxies \citep{Ricotti16}.
+The Pop II stars all tend to cluster within 1 kpc of the center of the halo, while the Pop III stars are more dispersed throughout the halo.
+
+This halo merges with a neighboring smaller halo that has formed its own distribution of Pop III and II stars, which is where a majority of the stars that fell in came from.
+This results in a mix of stars that reside within the final halo, those that formed within the main progenitor, and those that formed outside.
+This can be seen in Figure \ref{fig:og_evolution}, where Pop III and Pop II stars form within 5 kpc of the main halo, and end up combining within the final halo at $z = 10$.
+This feature will be of particular interest in the NSM runs.
+
+By $z = 10$, the halo has a Pop II stellar mass of $\sim 10^{4.4} \Ms$ and a living Pop III stellar mass of $\sim 978 \Ms$.
 At this time, there are still 14 Pop III stars living within the halo, concurrently with Pop II stars.
@@
 The general dynamics of the halo remain unchanged, and the main halos in the NSM runs looks visually similar to the halo in the original run.
-Run D, Fiducial, and E have Pop II stellar masses of $10^{5.27}$, $10^{4.87}$, and $10^{4.80}$ \Ms{}, at $z = 10$ respectively, i.e.
+Run D ($10^{50}$ erg), Fiducial ($10^{50.5}$ erg), and E ($10^{51}$ erg) have Pop II stellar masses of $10^{5.27}$, $10^{4.87}$, and $10^{4.80}$ \Ms{}, at $z = 10$ respectively, i.e.
 the lowest energy run produces the highest Pop II stellar mass.
-The median and mean mass weighted creation times for the Pop II stars that form within the halo for runs D, Fiducial, and E are 462 Myr ($z = 10.2$) and 455 Myr ($z = 10.3$), 456 Myr ($z = 10.3$) and 443 Myr ($z = 10.5$), and 443 ($z = 10.5$) Myr and 436 Myr ($z = 10.6$) respectively.
-The mean creation time for Pop II stars in these runs is higher than the mean creation time in the original run.
-Runs D and Fiducial form 2 Pop III stars at 151 Myr ($z = 22.6$) and 353 Myr ($z = 12.4$) and at 151 Myr ($z = 22.6$) and 266 Myr ($z = 15.2$), with masses of 26.5 \Ms{} and 27.7 \Ms{}, and 26.5 \Ms{} and 30.4 \Ms, respectively.
+The median and mean mass weighted creation times for the Pop II stars that form within the halo for runs D, Fiducial, and E are 462 Myr ($z = 10.2$) and 455 Myr ($z = 10.3$), 456 Myr ($z = 10.3$) and 443 Myr ($z = 10.5$), and 443 Myr ($z = 10.5$) and 436 Myr ($z = 10.6$) respectively.
+The mean creation time for Pop II stars in these runs is higher than the mean creation time of 402 Myr in the original run.
+In the main progenitor, runs D and Fiducial form two Pop III stars at 151 Myr ($z = 22.6$) and 353 Myr ($z = 12.4$) and at 151 Myr ($z = 22.6$) and 266 Myr ($z = 15.2$), with masses of 26.5 \Ms{} and 27.7 \Ms{}, and 26.5 \Ms{} and 30.4 \Ms, respectively.
 Run E produces only one Pop III star at 151 Myr ($z = 22.6$) with a mass of 26.5 \Ms{}.
@@
 
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
+	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original run.
+The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.
+The NSM occurs at 286 Myr.}
+	\label{fig:eng_evol}
+\end{figure}
+
 We show the halo mass, Pop II stellar mass, gas fraction, and r-process mass of the most massive halo progenitor in Figure \ref{fig:eng_evol}.
-Halo masses in each run are almost identical to each other, and with runs D, Fiducial, and E growing to $10^{8.3} \Ms$ and the original run to $10^{8.2} \Ms$.
+As expected, halo masses in each run are almost identical to each other, and with runs D, Fiducial, and E growing to $10^{8.3} \Ms$ and the original run to $10^{8.2} \Ms$.
 The Pop II stellar mass follows a relatively similar trend in each run, but the NSM runs end with larger Pop II stellar masses as compared to the original run.
@@
 The r-process mass in each run slowly decreases as star formation takes place and some of the r-process material is deposited into star particles.
-
+\begin{figure*} 
+	\includegraphics[width=\textwidth]{plots/eng_NSM_evolution.pdf}
+	\caption[R-process metallicity projections of the explosion energy variation runs through time.]{Evolution of the density-weighted projections of the r-process metallicity for each explosion energy variation run.
+The first column shows the system at $z = 14.4$, when the NSM event takes place, the middle column shows $z = 12$, and the right column shows the final output at $z = 10$.
+The top row shows run D, the middle shows the Fiducial run, and the bottom shows run E.
+The white circle indicates the virial radius of the halo.
+The yellow dots show Pop III stars, and the aqua dots show Pop II stars.
+The white dot indicates the chosen Pop III star that produced the NSM event.
+Note that the star particles are covering the NSM explosion in the lowest and Fiducial runs at the first timestep.}
+	\label{fig:eng_met4_evol}
+\end{figure*}
 The evolution of the r-process metallicity field can be seen in Figure \ref{fig:eng_met4_evol}.
@@
 This means that a metallicity of 1 $Z_{\mathrm{r}}$ is equal to the r-process abundances within the solar system.
-
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
-	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original run.
-The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.}
-	\label{fig:eng_evol}
-\end{figure}
-
-\begin{figure*} 
-	\includegraphics[width=\textwidth]{plots/eng_NSM_evolution.pdf}
-	\caption[R-process metallicity projections of the explosion energy variation runs through time.]{Evolution of the density-weighted projections of the r-process metallicity for each explosion energy variation run.
-The first column shows the system at $z = 14.4$, when the NSM event takes place, the middle column shows $z = 12$, and the right column shows the final output at $z = 10$.
-The top row shows run D, the middle shows the Fiducial run, and the bottom shows run E.
-The white circle indicates the virial radius of the halo.
-The yellow dots show Pop III stars, and the aqua dots show Pop II stars.
-The white dot indicates the chosen Pop III star that produced the NSM event.
-Note that the star particles are covering the NSM explosion in the lowest and Fiducial runs at the first timestep.}
-	\label{fig:eng_met4_evol}
-\end{figure*}
 
@@
 Runs A, B and Fiducial vary the delay time of the NSM by 10, 30 and 100 Myr, respectively.
-The NSM occurs in runs A, B and Fiducial at 197 Myr ($z = 18.7$), 216 Myr ($z = 17.6$) and 286 Myr ($z = 14.4$), respectively.
+The NSM occurs in runs A, B and Fiducial at 196 Myr ($z = 18.7$), 216 Myr ($z = 17.6$) and 286 Myr ($z = 14.4$), respectively.
 Similar to the energy variation runs, the dynamics and visual appearance of the halos remains similar to the original run.
@@
 We refer the reader to the top of the previous section for a reminder of these values for the Fiducial run.
+
+\begin{figure} 
+	\includegraphics[width=\columnwidth]{plots/time_evolution.pdf}
+	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for each delay time variation run.]{The evolution of the main halo in each delay time variation run and the original run.
+The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.
+The NSM occurs at 196 Myr, 216 Myr, and 286 Myr for runs A, B, and Fiducial, respectively,}
+	\label{fig:time_evol}
+\end{figure}
 
@@
 
-The evolution of the r-process metallicity field can be seen in Figure \ref{fig:time_met4_evol}.
-The top row represents run A, the middle run B, and the bottom the Fiducial run.
-The first column shows the timestep when the NSM takes place, which occurs at different times for these runs, based on their delay time.
-The middle column shows $z = 12$, and the right column shows the final redshift at $z = 10$.
-When the NSM occurs in run A, because the halo is so small at this early time, the r-process material is not contained within the halo, but extends outside of the halo.
-By $z = 12$, there are a number of Pop III stars that go SN and Pop II stars that form just outside of the halo, all of which pushes the gas outside of the halo even further through external feedback.
-As time progresses, some of the r-process material is recovered, but a large tail, or wing like structure remains outside of the halo.
-Run B follows a similar story as run A, with a similar structure appearing at $z = 10$.
-The total r-process mass is similar for these two runs by the end of the simulation.
-These short delay times appear very different as compared to the longer delay time, where the r-process material is always fully contained within the halo.
-
-\begin{figure} 
-	\includegraphics[width=\columnwidth]{plots/time_evolution.pdf}
-	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for each delay time variation run.]{The evolution of the main halo in each delay time variation run and the original run.
-The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.}
-	\label{fig:time_evol}
-\end{figure}
-
 \begin{figure*} 
@@
 
+The evolution of the r-process metallicity field can be seen in Figure \ref{fig:time_met4_evol}.
+The top row represents run A, the middle run B, and the bottom the Fiducial run.
+The first column shows the timestep when the NSM takes place, which occurs at different times for these runs, based on their delay time.
+The middle column shows $z = 12$, and the right column shows the final redshift at $z = 10$.
+When the NSM occurs in run A, because the halo is so small at this early time, the r-process material is not contained within the halo, but extends outside of the halo.
+By $z = 12$, there are a number of Pop III stars that go SN and Pop II stars that form just outside of the halo, all of which pushes the gas outside of the halo even further through external feedback.
+As time progresses, some of the r-process material is recovered, but a large tail, or wing like structure remains outside of the halo.
+Run B follows a similar story as run A, with a similar structure appearing at $z = 10$.
+The total r-process mass is similar for these two runs by the end of the simulation.
+These short delay times appear very different as compared to the longer delay time, where the r-process material is always fully contained within the halo.
+
 Similar to the energy variation runs, the time delay runs lead to significantly higher Pop II stellar masses as compared to the original run.
 Runs A, B, and Fiducial end with Pop II stellar masses of $10^{5.25}\Ms$, $10^{5.58} \Ms$, and $10^{4.87}$ \Ms.
-Run A also produces 6 Pop III stars within the main halo progenitor, which is the highest number of Pop III stars formed within the main halo of all the runs.
+Run A also produces six Pop III stars within the main halo progenitor, which is the highest number of Pop III stars formed within the main halo of all the runs.
 Table \ref{tab:time_stellar} presents this information in the first two columns.
@@
 \begin{itemize}
-	\item NSMs do lead to a substantial fraction of highly r-process enhanced Pop II stars.
+	\item NSMs originating from Pop III stars do lead to a substantial fraction of highly r-process enhanced Pop II stars.
 	\item When the explosion energy is high, 74\% of stars are highly r-process enhanced, versus when the explosion energy is lower, only 63\% are highly r-process enhanced. 
@@
 	\item The shorter time delays still lead to a high mass fraction of r-process enhanced stars, but a smaller fraction of highly r-process enhanced stars.
-	\item The half-mass radius significantly decreases in each NSM run due to the large number of Pop II stars that form and cluster near the center of the halo. 
-	\item Star formation and feedback that occurs in and around the halo heavily governs the dynamics and details of star formation in these runs.
+	\item The half-mass radius significantly decreases in each NSM run due to the large number of Pop II stars that form and cluster near the center of the halo at the end of the simulation. 
+	\item Star formation and feedback that occur in and around the halo heavily govern the dynamics and details of star formation in these runs.
 A larger sample size of galaxies with NSMs is needed in order to more fully understand the impact of a NSM on the second generation of stars.

### 2023-07-14 NSM_mixing.tex
Fixing plots and short title

@@
 % Keep the title short and informative.
-\title[NSMs from Pop III stars]{Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe}
+\title[Neutron Star Mergers from Population III Stars]{Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe}
 
@@
 The Jeans length is always resolved by at least four cells.
-We use the cosmological parameters from the Planck Collaboration (2020) \citep{Planck18_Cosmo}: $\Omega_{\mathrm{M}} = 0.3111$, $\Omega_{\Lambda} = 0.6889$, $\Omega_{\mathrm{DM}} = 0.262125$, and $h = 0.6766$, with the parameters defined as their usual definitions.
+We use the cosmological parameters from the Planck Collaboration (2020) \citep{Planck18_Cosmo}: $\Omega_{\mathrm{M}} = 0.3111$, $\Omega_{\Lambda} = 0.6889$, $\Omega_{\mathrm{DM}} = 0.262125$, $\Omega_{\mathrm{b}} = 0.04897$ and $h = 0.6766$, with the parameters defined as their usual definitions.
 
@@
 The Pop III star that we chose has an initial mass of $28.7 M_{\odot}$ that was randomly selected from an IMF described in \citet{Skinner20}.
-The chosen Pop III star is then converted into a symmetric Pop III binary system with component masses of $\sim 14.35 M_{\odot}$, but is still modelled as a single star particle with an ionizing hydrogen photon rate of $2.9 \times 10^{48} [\mathrm{s}^{-1}]$, which is equal to the sum of the two individual stellar photon rates from \citet{Schaerer02}.
+The chosen Pop III star is then converted into a symmetric Pop III binary system with component masses of $\sim 14.35 M_{\odot}$, but is still modelled as a single star particle with an ionizing hydrogen photon rate of $2.9 \times 10^{48} \mathrm{s}^{-1}$, which is equal to the sum of the two individual stellar photon rates from \citet{Schaerer02}.
 
@@
 
-DS is supported by the NASA FINESST fellowship award 80NSSC20K1540. The figures in this paper were constructed with the plotting library \textsc{matplotlib} \citep{matplotlib}.
+DS is supported by the NASA FINESST fellowship award 80NSSC20K1540.
+The figures in this paper were constructed with the plotting library \textsc{matplotlib} \citep{matplotlib}.
+JHW is supported by NSF grants OAC-1835213 and AST-2108020 and NASA grants 80NSSC20K0520 and 80NSSC21K1053.
 

### 2023-07-14 NSM_mixing.tex
Updating Zr values, adding information about how to convert to [X/H].

@@
 
-To better represent the r-process metallicity, we define a new unit $Z_{\mathrm{r}} = 1.6 \times 10^{-10}$ which is scaled to the r-process abundances of the solar system from \citet{Goriely99}, normalized by the solar system H abundance.
+To better represent the r-process metallicity, we define a new unit $Z_{\mathrm{r}} = 0.01384$ which is scaled to the r-process abundances of the solar system from \citet{Goriely99}, normalized by the solar system Si abundance.
 This means that a metallicity of 1 $Z_{\mathrm{r}}$ is equal to the r-process abundances within the solar system.
+To convert from $Z_{\mathrm{r}}$ to an abundance ratio of [X/H] for some element X, one can use $[X/H] = [X/H]_{\mathrm{r}} + A(X)_{\odot, r} - A(X)_{\odot}$ to normalize to an r-process solar composition \cite[see Step \#3 in Table 2 of][for an excellent description of metallicity conversions]{Hinkel22}.
+Here, $[X/H]_{\mathrm{r}} = v_{x} + \mathrm{log}(Z_{\mathrm{r}})$, where $v_{x}$ is open to the reader, depending on their choice of NSM ejecta yields.
+This makes $[X/H] = v_{x} + \mathrm{log}(Z_{\mathrm{r}}) + A(X)_{\odot, r} - A(X)_{\odot}$.
+To compare with results from \citet{Frebel23}, we put this in terms of abundances from \citet{Lodders09} (L09) and \citet{Roederer22} (R22) as collected by \citet{Frebel23} (see their Table 2).
+In terms of these values, $[X/H] = v_{x} + \mathrm{log}(Z_{\mathrm{r}}) + \mathrm{log} \epsilon_{\mathrm{R22}} (X) - \mathrm{log} \epsilon_{\mathrm{L09}} (X)$.
+For Ba, the difference between the abundances from \citet{Frebel23} is -0.92 and for Eu, the difference between the abundances is -0.12.
 
@@
 		\hline
-		Fiducial & 2 & $10^{4.87}$ & 80\% & 80\% \\
-		D & 2 & $10^{5.27}$ & 91\% & 63\% \\
-		E & 1 & $10^{4.80}$ & 74\% & 74\% \\
+		Fiducial & 2 & $10^{4.87}$ & 80\% & 64\% \\
+		D & 2 & $10^{5.27}$ & 80\% & 14\% \\
+		E & 1 & $10^{4.80}$ & 74\% & 72\% \\
 		Original & 2 & $10^{4.52}$ & -- & -- \\
@@
 	\caption[Information about the stellar populations within the explosion energy variation runs.]{Information about the stellar populations within the explosion energy variation runs.
-For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-8} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
+For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-6} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
 	\label{tab:eng_stellar}
@@
 Figure \ref{fig:eng_NSM_deltat} shows the r-process metallicity of the Pop II stars that formed within the halo as a function of their creation time relative to the NSM event.
-We define stars to be ``highly r-process enhanced'' if they have a metallicity of $> 10^{-1} Z_{\mathrm{r}}$ and to be ``r-process enhanced'' if they have a metallicity of $> 10^{-8} Z_{\mathrm{r}}$.
-At $z = 10$, we find that runs D, Fiducial and E have Pop II mass fractions of 80\%, 91\% and 74\% being r-process enhanced, and Pop II mass fractions of 80\%, 63\%, and 74\% being highly r-process enhanced, respectively.
-The lowest explosion energy results in a lower percentage of highly r-process enhanced stars, but the highest percentage of r-process enhanced stars overall.
+We define stars to be ``highly r-process enhanced'' if they have a metallicity of $> 10^{-1} Z_{\mathrm{r}}$ and to be ``r-process enhanced'' if they have a metallicity of $> 10^{-6} Z_{\mathrm{r}}$.
+At $z = 10$, we find that runs D, Fiducial and E have Pop II mass fractions of 80\%, 80\% and 74\% being r-process enhanced, and Pop II mass fractions of 14\%, 63\%, and 72\% being highly r-process enhanced, respectively.
+The lowest explosion energy results in a lower percentage of highly r-process enhanced stars, but a similar percentage of r-process enhanced stars compared to the higher explosion energy runs.
 As the energy increases, all Pop II stars that are enriched by the NSM are highly enhanced.
@@
 		\hline
-		Fiducial & 2 & $10^{4.87}$ & 80\% & 80\% \\
-		A & 6 & $10^{5.25}$ & 79\% & 50\% \\
-		B & 3 & $10^{5.58}$ & 80\% & 24\% \\
+		Fiducial & 2 & $10^{4.87}$ & 80\% & 64\% \\
+		A & 6 & $10^{5.25}$ & 70\% & 5\% \\
+		B & 3 & $10^{5.58}$ & 74\% & 0.2\% \\
 		Original & 2 & $10^{4.52}$ & -- & -- \\
@@
 	\caption[Information about the stellar populations within the delay time variation runs.]{Information about the stellar populations within the delay time variation runs.
-For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-8} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
+For each run, we list the number of Pop III stars that form, the total Pop II stellar mass at the final redshift, the mass fraction of Pop II stars that are r-process enhanced ($> 10^{-6} Z_{\mathrm{r}}$), and the mass fraction of Pop II stars that are highly r-process enhanced ($> 10^{-1} Z_{\mathrm{r}}$).}
 	\label{tab:time_stellar}
@@
 In this run, there hasn't been enough time for the material to escape the halo before Pop II Stars form, therefore, higher r-process metallicities are expected.
-We find that run A results in a 79\% and 50\% of the Pop II mass fraction being r-process enhanced and highly r-process enhanced, run B resulting in 80\% and 24\%, and run Fiducial resulting in 80\% and 80\% of the Pop II stars being r-process enhanced and highly r-process enhanced, respectively.
-This indicates that the NSM is in general enhancing a similar percentage of Pop II stars with r-process material, but the shorter delay times result in a smaller percentage of Pop II stars being highly r-process enhanced.
+We find that run A results in a 70\% and 5\% of the Pop II mass fraction being r-process enhanced and highly r-process enhanced, run B resulting in 74\% and 0.02\%, and run Fiducial resulting in 80\% and 64\% of the Pop II stars being r-process enhanced and highly r-process enhanced, respectively.
+This indicates that the NSM is in general enhancing a similar percentage of Pop II stars with r-process material, but the shorter delay times result in a much smaller percentage of Pop II stars being highly r-process enhanced.
 
@@
 	\item NSMs originating from Pop III stars do lead to a substantial fraction of highly r-process enhanced Pop II stars.
-	\item When the explosion energy is high, 74\% of stars are highly r-process enhanced, versus when the explosion energy is lower, only 63\% are highly r-process enhanced. 
+	\item When the explosion energy is high, 73\% of stars are highly r-process enhanced, versus when the explosion energy is lower, only 14\% are highly r-process enhanced. 
 	\item The lower explosion energy leads to a higher fraction of Pop II stars being r-process enhanced overall, but at lower metallicities in general.
-The higher explosion energy leads to a smaller fraction of r-process enhanced stars, but all that are enhanced are highly enhanced.
+The higher explosion energy leads to a smaller fraction of r-process enhanced stars, but almost all that are enhanced are highly enhanced.
 	\item The longer time delays lead to higher mass fractions of highly r-process enhanced stars, due to the NSM occurring closer to the period of Pop II star formation. 
-	\item The shorter time delays still lead to a high mass fraction of r-process enhanced stars, but a smaller fraction of highly r-process enhanced stars.
+	\item The shorter time delays still lead to a high mass fraction of r-process enhanced stars, but a much smaller fraction of highly r-process enhanced stars.
 	\item The half-mass radius significantly decreases in each NSM run due to the large number of Pop II stars that form and cluster near the center of the halo at the end of the simulation. 

### 2023-07-17 NSM_mixing.tex
Making a few edits. Final draft.

@@
 We find that in general, a NSM leads to a significant r-process enhancement in the second generation of stars.
-A high explosion energy leads to all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced.
-When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly r-process enhanced.
+A high explosion energy leads to almost all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced.
+When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly r-process enhanced compared to longer delay times.
 This work represents a stepping stone towards understanding how these events impact their environments and metal abundances of descendant generations of stars.
@@
 The GW170817 event was detected by LIGO, and along with it came a kilonova, a transient burst of energy powered by radioactive decay, making this event a multimessenger astronomical affair.
-LIGO detected a NSM with components in the mass range of $1.17 - 1.60 \Ms$ \citep{Abbott17}, and a $\gamma$-ray burst 1.7 seconds after the merger was detected by the Fermi Gamma-ray Burst Monitor \citep{Goldstein17}.
+LIGO detected this NSM with components in the mass range of $1.17 - 1.60 \Ms$ \citep{Abbott17}, and a $\gamma$-ray burst 1.7 seconds after the merger was detected by the Fermi Gamma-ray Burst Monitor \citep{Goldstein17}.
 This allowed for precise sky localization and a massive follow up effort from telescopes across the electromagnetic spectrum \citep[see][for an extensive review of this follow-up]{Abbott17a}.
@@
 Out of this massive follow-up campaign came analysis of the light curve of the kilonova in the UV, optical, and IR \citep{Drout17, Pian17}.
-\citet{Drout17} found that this kilonova, was in fact powered by radioactive decay of r-process elements.
+\citet{Drout17} found that this kilonova was in fact powered by radioactive decay of r-process elements.
 They estimate that $\sim 0.05 \Ms$ of enriched, r-process material must have been ejected from this event.
@@
 We run a total of six simulations, five with a NSM model and one without.
-The run without the NSM model was run first, and the following five NSM simulations are run based on the non-NSM (original) simulation.
+The run without the NSM model was run first, and the following five NSM simulations were run based on the non-NSM (original) simulation.
 The original simulation has a domain width of 1 comoving Mpc and a root grid of $64^{3}$ cells.
@@
 The lowest explosion energy results in a lower percentage of highly r-process enhanced stars, but a similar percentage of r-process enhanced stars compared to the higher explosion energy runs.
-As the energy increases, all Pop II stars that are enriched by the NSM are highly enhanced.
+As the energy increases, almost all Pop II stars that are enriched by the NSM are highly enhanced.
 This is due to the large amount of Pop II stars that form at late times near the center of the halo, where the majority of the r-process enhanced gas is contained.

### 2023-07-18 NSM_mixing.tex
Minor proofreading edits

@@
 In terms of these values, $[X/H] = v_{x} + \mathrm{log}(Z_{\mathrm{r}}) + \mathrm{log} \epsilon_{\mathrm{R22}} (X) - \mathrm{log} \epsilon_{\mathrm{L09}} (X)$.
-For Ba, the difference between the abundances from \citet{Frebel23} is -0.92 and for Eu, the difference between the abundances is -0.12.
+For Ba, the difference between the abundances from \citet{Frebel23} is --0.92 and for Eu, the difference between the abundances is --0.12.
 
@@
 	\caption[R-process metallicity as a function of $\Delta t_{\mathrm{NSM}}$ for the energy variation runs.]{The r-process metallicity for Pop II stars that formed in the halo as a function of when they formed relative to the NSM.
-The blue stars indicate Pop II stars formed in run D, the orange diamonds from run Fiducial, and the green squares from run E.
+The blue stars indicate Pop II stars formed in run D, the green diamonds from run Fiducial, and the yellow squares from run E.
 We have artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$ for clarity.}
@@
 	\caption[R-process metallicity fraction as a function of $\Delta t_{\mathrm{NSM}}$ for the delay time variation runs.]{The r-process metallicity for Pop II stars that formed in the halo as a function of when they formed relative to the NSM.
-The blue stars indicate Pop II stars formed in run A, the orange diamonds from run B, and the green squares from run Fiducial.
+The blue stars indicate Pop II stars formed in run A, the green diamonds from run B, and the yellow squares from run Fiducial.
 We have artificially raised the metallicity fraction for stars that have metallicity fractions below a value of $10^{-6}$ for clarity.}

### 2023-07-18 NSM_Skinner_Wise/NSM_mixing.tex
Added separate directory for arXiv submission. Added Data Availability section and adjusted abstract to fit the word limit.

--- 2023-07-18 NSM_mixing.tex
@@
 \usepackage{mathtools}
+\usepackage{orcidlink}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author[Skinner \& Wise]{
-Danielle Skinner,$^{1}$\thanks{E-mail: drenniks@gatech.edu}
-John H. Wise$^{1}$
+Danielle Skinner$^{\orcidlink{0000-0002-5346-1308}}$$^{1}$\thanks{E-mail: drenniks@gatech.edu},
+John H. Wise$^{\orcidlink{0000-0003-1173-8847}}$$^{1}$
 \\
@@
 The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants.
-These compact objects can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to take place.
-In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution in order to understand the impact on the second generation of stars and their metal abundances.
+These remnants can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to occur.
+In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances.
 We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time.
-We find that in general, a NSM leads to a significant r-process enhancement in the second generation of stars.
-A high explosion energy leads to almost all enhanced r-process stars being highly r-process enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly r-process enhanced.
-When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly r-process enhanced compared to longer delay times.
-This work represents a stepping stone towards understanding how these events impact their environments and metal abundances of descendant generations of stars.
+In general, a NSM leads to a significant r-process enhancement in the second generation of stars.
+A high explosion energy leads to almost all enhanced r-process stars being highly enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly enhanced.
+When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly enhanced compared to longer delay times.
+This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
 \end{abstract}
@@
 
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+The data presented in this work is available upon reasonable request to the corresponding author.
 

### 2023-08-31 NSM_Skinner_Wise/referee/referee_response.tex
Adding referee response.

\documentclass[11pt]{article}
%\renewcommand\refname{ }

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}

\input macros.tex

\begin{document}

\begin{center} 
\bfseries{
\begin{large}
  Response to referee report for manuscript ref. MN-23-2721-MJ
\end{large}
}
\end{center}

\begin{tcolorbox}[colback={lightgray}]
    The authors focus on the impacts of the neutron star merger (NSM) on the formation of second-generation stars in first galaxies. Following r-process elements with cosmological simulations is unique and interesting. However, important information about the modeling NSM is lacking in the current manuscript. Also, consideration of the simulation results is not enough. I hope the authors revise the manuscript based on the following comments.
\end{tcolorbox}

We thank the referee for their review of our work, and we have
addressed their points individually below.  In the manuscript, we have
boldfaced the added text and crossed out the deleted text.

\begin{tcolorbox}[colback={lightgray}]
    1)      The authors assume that neutron star binaries merge after 10, 30, or 100 Myr. These time scales are too short (Belczynski et al. 2002, ApJ, 572, 407; Kinugawa et al. 2014, MNRAS, 442, 2963). What kind of binary parameters did you assume? Is it reasonable? Without reasonable explanations about the short merger timescales, I cannot believe that NSMs happened in the early Universe.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    2)      NS binaries can form even in Population I/II stars, particularly in dense star clusters. Why do you consider NS binaries originated from Population III stars. The binary fraction and ISM of population III stars are still under debate. The authors should describe the motivation of NSM originating from population III stars.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    3)      The current abstract consists of a general introduction and expectable trends. The authors should rewrite the text of the abstract significantly with solid conclusions and values taken from the detailed simulations.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    4)      It looks like one of the main points of the manuscript is revealing the impacts of NSM on the physical properties of the first galaxies with Pop II star formation. An NSM is an additional feedback source at the point of the first galaxy formation. I think the impact of NSM is degenerated with other factors of Pop III stars like the number of stars in mini-haloes, star formation efficiency, and initial mass function. For example, if three Pop III stars form in mini-halos (e.g., Sugimura et al. 2020, ApJ, 892, L14; Sugimura et al. 2023), they are likely to give similar feedback. The authors should add a discussion about the uniqueness of NSMs at the point of the first galaxy formation.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}] 
    5)      Considerations about the simulation results are not enough. For example, in Sec. 3.2, the authors say, “The Pop II stellar mass follows a relatively similar trend in each run, but the NSM runs end with larger Pop II stellar masses as compared to the original run.” Why do NSMs induce the larger Pop II stellar masses? Please describe the physical reasons because it is complicated due to a combination of more metal enrichment and gas blowout.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    Minor comments:
    6)      Is Sec. 3.1. about the original (without NSM) run? It would be better to write it.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    7)      Figure 6 shows “P3 metallicity fraction”. What is the P3 metallicity?
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    8)      Purple lines in Figures 3, 5, and 8 show “Hyp.”. What is the meaning of Hyp.?
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]
    9)      The authors show the coexistence of Pop II and III stars in the first galaxies. Recent theoretical studies showed similar results (Riaz et al. 2022, ApJL, 937, L6; Yajima et al., arXiv2211.12970). It would be good to discuss the mass fraction and distribution of Pop III stars in the first galaxies with the previous works. 
\end{tcolorbox}

We again thank the referee for the insightful review that helped
improve our paper.

\end{document}

### 2023-08-31 NSM_Skinner_Wise/referee/referee_response.tex
Adding initial thoughts, responses, to the referee report.

@@
 \usepackage{tcolorbox}
+\usepackage{natbib}
 
@@
 
+We agree that the time scales we have explored are very short, but we are exploring a very particular scenario, and the delay times that we have chosen are not yet out of the realm of possibilities.
+\citet{Hirai15} quote the lower limit of a delay time to be $~10$ Myr, and that delay times of $~100$ Myr can explain the scatter in [Eu/Fe] for metal-poor stars in the galactic halo.
+
+\citet{Frebel23} also summarize the current state of discussion around the merger times for NSMs.
+They quote the minimum delay time to be between 10-100 Myr based on work done by other authors, and that there is some discussion that even shorter delay times of about 1 Myr could be possible.
+
+For Reticulum II (Ret II) in particular, a long delay time of a couple Gyr is not compatible with the r-process enhanced stars.
+\citet{Simon23} provide an explanation for the timing requirements for r-process enrichment in Ret II, and they find that a NSM must occur with 500 Myr in order to reproduce the abundances and allow for thorough mixing.
+This requires the NSM to occur well before the formation of second generation stars.
+
+Enzo does not have the capability to follow binary system formation.
+We simply do not have the resolution to accomplish such a task.
+Because of this, our NSM is an extremely ideal scenario, where we do not have to pick binary system parameters.
+The question of how this binary system formed in the first place is outside of the scope of this paper and would require significant contributions to the code base in order for that to happen in our simulations.
+We are simply assuming that there could exist a possibility where this type of binary system could form and then go on to merge together.
+Based on work cited above, we are comfortable with the delay times we have chosen, and they could add further information about the possibility of these short time delays moving forward.
+
+We are certainly simulating a particular scenario.
+We are operating under the assumption that if a NSM did occur in a galaxy like Ret II, then it would have to happen fairly early in order to allow for enough time to pass for thorough mixing to take place.
+We would also like to remind the referee that this is a "proof-of-concept" test of our model to see how the NSM may affect the second generation of stars.
+We aren't trying to exactly reproduce Ret II, but we want to begin to understand what the effects of a NSM of this type would look like early in the history of a galaxy.
+We would like to let the referee know that there is a follow up plan to this simulation, with more papers to come.
+
+\textbf{(DS to-do)} We have added this explanation to SECTION.
+
+\textbf{DS Notes:}
+
+https://arxiv.org/pdf/2212.00810.pdf
+\begin{itemize}
+    \item for reticulum II, longer delay times (~couple Gyr) are incompatible with r-process stars in Ret II
+    \item must merge within about 500 Myr for Ret II
+    \item there is uniformity among the r-process enriched stars, indicating that thorough mixing needs to take place before star formation can occur.
+To allow for enough time, the NSM has to happen relatively early in the star formation history of ret II
+\end{itemize}
+
+https://arxiv.org/pdf/2302.09188.pdf
+\begin{itemize}
+    \item minimum delay time of 10-100 Myr
+    \item there is some argument that merging could happen on the order of 1 Myr
+    \item still lots of debate around the specifics
+\end{itemize}
+
 \begin{tcolorbox}[colback={lightgray}]
@@
 
+The motivation of this work came from the results of the r-process enhanced stars in Ret II.
+For these stars, a NSM occurring early in the star formation history of the galaxy can explain the enhancement.
+We were interested in the possibility of the NSM occurring early enough in the history of the galaxy to be a descendant of Pop III stars.
+We ask this question near the end of the Introduction: "...
+what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?" This is the question that we are exploring in this work.
+
+We do not consider any binary system formation for Pop II stars in this work, mainly because Enzo does not currently have the capability to model binary systems for these stars.
+To keep things simple, we are only considering the binary system formation, and subsequent merging, of the NSs.
+This would be an interesting thing to explore in the future however.
+
+\textbf{(DS to-do)} We have made our motivation more clear in SECTION.
+
 \begin{tcolorbox}[colback={lightgray}]
@@
 \end{tcolorbox}
+
+\textbf{DS Notes:}
+Replace two general sentences with these more specific ones.
+\begin{itemize}
+    \item A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
+    \item When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.
+\end{itemize}
 
@@
 
+\textbf{DS Notes:}
+\begin{itemize}
+    \item I feel like the main thing that makes NSM unique is their production of r-process elements (along with the effects of a kilonova, but maybe we don't mention that?).
+One of the main points is that NSMs can produce r-process enhanced stars, but also that the exact feedback mechanisms that occur appear to drastically affect results (last bullet point in conclusions).
+So we cannot pick apart the impacts of NSM on the physical properties of the first galaxies with Pop II star formation -- this was not something that we were trying to address really at all?
+\end{itemize}
+
 \begin{tcolorbox}[colback={lightgray}] 
@@
 
+\textbf{DS Notes:}
+\begin{itemize}
+    \item Yes, this is a good question and one that I thought we made pretty clear.
+The answer to this is "I don't know".
+There are a lot of details to pick through in these simulations, and making comparisons across the simulations is a complicated task.
+Because we don't have a large sample size to study, it's hard to say anything conclusive about how the NSM might affect the Pop II stellar masses, and whether other star formation and feedback is affecting it as well.
+This is a question we are continuing to explore.
+In this paper, we are simply reporting on the results.
+    \item We did find that NSM runs have higher cold gas mass fractions at late times. This could be one possible explanation for this.
+\end{itemize}
+
 \begin{tcolorbox}[colback={lightgray}]
@@
 
+\textbf{(DS to-do)} Yes, Sec. 3.1 is about the original run. We have changed this section title to reflect that.
+
 \begin{tcolorbox}[colback={lightgray}]
@@
 
+\textbf{(DS to-do)}
+
 \begin{tcolorbox}[colback={lightgray}]
@@
 \end{tcolorbox}
+
+\textbf{(DS to-do)} We apologize for that confusion, we have change that to say "OG" in the plots. Hyp. stood for "hypernova" which is how the original Pop III star ends its life.
 
@@
 
+\textbf{DS Notes:}
+\begin{itemize}
+    \item I think I will need to grab the masses of Pop III stars in the halo, but I can do this pretty quickly.
+    \item Riaz+22: compare with their Figure 1, 2, and 3
+    \item Yajima+23: compare with their Figure 2, 4, third bullet point in their conclusion
+\end{itemize}
+
 We again thank the referee for the insightful review that helped
@@
 
+\bibliographystyle{plainnat}
+\bibliography{drenniks}
+
 \end{document}

### 2023-08-31 NSM_Skinner_Wise/referee/referee_response.tex
Fixing up minor items or adding info to the referee report.

@@
 
-\textbf{(DS to-do)} Yes, Sec. 3.1 is about the original run. We have changed this section title to reflect that.
+Yes, Sec. 3.1 is about the original run. We have changed this section title and added a bit of text to reflect that.
 
@@
 
-\textbf{(DS to-do)}
+We apologize for this, the caption was correct, but the label in the plot was wrong.
+The label should have read "Total Metallicity Fraction" instead of "P3 Metallicity Fraction".
+The total metallicity is the metallicity of the stars from both Pop II and Pop III sources.
+We have fixed this plot.
 
@@
 
-\textbf{(DS to-do)} We apologize for that confusion, we have change that to say "OG" in the plots. Hyp. stood for "hypernova" which is how the original Pop III star ends its life.
+We apologize for that confusion.
+"Hyp." stood for "hypernova" which is how the original Pop III star ends its life.
+To keep things simple, we have changed that in the plots to say "OG" to make it clear that those lines correspond to the original run with no NSM.
 
@@
 \begin{itemize}
-    \item I think I will need to grab the masses of Pop III stars in the halo, but I can do this pretty quickly.
-    \item Riaz+22: compare with their Figure 1, 2, and 3
-    \item Yajima+23: compare with their Figure 2, 4, third bullet point in their conclusion
+    \item Riaz+22: compare with their Figure 1 and 3
+    \begin{itemize}
+        \item Re.
+Figure 1: Looking at the redshift range between 10 and 20, and comparing with their halo masses between $10^7 - 10^9 M_\odot$ since this is the closest out halo gets to by the end of the simulation, we do see much higher stellar masses compared to them.
+For example, at z = 10, they see $10^3 - 10^5 M_\odot$ for Pop II stars and $10^1 - 10^2 M_\odot$ for Pop III stars.
+For us, at z = 10 we see a few $\times 10^4 M_\odot$ for Pop II stars (which aligns with their results), and $~10^{3} M_{\odot}$ for Pop III stars, which is certainly larger than Riaz+22.
+However, they do give some generous ranges for the Pop II and Pop III stellar masses, so our results don't seem to be completely different from what they are saying.
+        \item Re. Figure 3: This figure is very similar to the one from Yajima+23. We do see similar ratios overall.
+    \end{itemize}
+    \item Yajima+23: compare with their Figure 4, third bullet point in their conclusion
+    \begin{itemize}
+        \item Re: Figure 4.
+I have made this same plot for our work.
+We have slightly lower values compared to Yajima.
+For all variation runs, for a stellar mass of $~10^{4.5} M_\odot$, we see a Pop III mass ratio of about $~10^{-1.5}$, as compared to Yajima's results of $~10^{-1}$.
+They have considerable scatter for their z = 10, 11, and 12 data.
+Certainly we see the same trend as them, as stellar mass increases, the ratio of Pop III stellar mass to total stellar mass decreases.
+We do see similar values at our maximum stellar mass value of $~10^{5.5} M_\odot$ having a mass ratio of $~10^{-2.25}$.
+An important thing to consider in this comparison is the much higher halo mass of their main halos.
+They look at a halo that grows to $5 \times 10^{11} M_\odot$ by z = 9.5, whereas our halo gets to $~2 \times 10^{8} M_\odot$ at z = 10.
+        \item Based on these results, we certainly agree with their third bullet point.
+In general, the mass fraction of Pop III stars is less than 0.01 for halos with stellar masses $> 10^{4} M_\odot$
+    \end{itemize}
 \end{itemize}

### 2023-08-31 NSM_Skinner_Wise/NSM_mixing.tex
Fixing up minor items or adding info to the referee report.

@@
 
-\subsection{Evolution of the main halo} \label{sec:main_halo}
+\subsection{Evolution of the main halo \textbf{in the original run}} \label{sec:main_halo}
 \begin{figure} 
@@
 
-The most massive progenitor of the main halo is first identified at $z = 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
+\textbf{In the original run with no NSM,} the most massive progenitor of the main halo is first identified at $z = 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
 During that time, the halo forms two Pop III stars with masses of 26.5 \Ms{} and 195.5 \Ms{} at 150.7 Myr ($z = 22.6$) and 286.1 Myr ($z = 14.4$), respectively.

### 2023-08-31 NSM_Skinner_Wise/referee/referee_response.tex
Adding some plots to the final comment.

@@
 \usepackage{natbib}
+\usepackage{subfig}
 
@@
 \textbf{DS Notes:}
+\begin{figure}[h]
+    \centering
+    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_pop3_ratio.pdf} }}%
+    \qquad
+    \subfloat[\centering Delay Time Variation]{{\includegraphics[width=0.4\textwidth]{plots/time_pop3_ratio.pdf} }}%
+    \caption{The mass fraction of Pop III stars to total stellar mass versus the total stellar mass colored by redshift.}%
+    \label{fig:ratio}%
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_stellar_mass.pdf} }}%
+    \qquad
+    \subfloat[\centering Delay Time Variation]{{\includegraphics[width=0.4\textwidth]{plots/time_stellar_mass.pdf} }}%
+    \caption{The total stellar mass of both Pop III and Pop II stars as a function of redshift.
+The solid lines are the total stellar masses of Pop III stars, and the dashed lines are total stellar masses of Pop II stars.}%
+    \label{fig:ratio}%
+\end{figure}
+
 \begin{itemize}
@@
 However, they do give some generous ranges for the Pop II and Pop III stellar masses, so our results don't seem to be completely different from what they are saying.
-        \item Re. Figure 3: This figure is very similar to the one from Yajima+23. We do see similar ratios overall.
+        \item Re. Figure 3: This figure is very similar to the one from Yajima+23. We do see similar ratios overall (see Figure \ref{fig:ratio} above).
     \end{itemize}
@@
 An important thing to consider in this comparison is the much higher halo mass of their main halos.
-They look at a halo that grows to $5 \times 10^{11} M_\odot$ by z = 9.5, whereas our halo gets to $~2 \times 10^{8} M_\odot$ at z = 10.
+They look at a halo that grows to $5 \times 10^{11} M_\odot$ by z = 9.5, whereas our halo gets to $~2 \times 10^{8} M_\odot$ at z = 10 (see Figure \ref{fig:ratio} above).
         \item Based on these results, we certainly agree with their third bullet point.

### 2023-08-31 NSM_Skinner_Wise/referee/referee_response.tex
Adding some links.

@@
 \begin{itemize}
-    \item Riaz+22: compare with their Figure 1 and 3
+    \item Riaz+22: compare with their Figure 1 and 3 (https://iopscience.iop.org/article/10.3847/2041-8213/ac8ea6/meta)
     \begin{itemize}
@@
     \end{itemize}
-    \item Yajima+23: compare with their Figure 4, third bullet point in their conclusion
+    \item Yajima+23: compare with their Figure 4, third bullet point in their conclusion (https://arxiv.org/pdf/2211.12970.pdf)
     \begin{itemize}

### 2023-09-11 NSM_Skinner_Wise/referee/referee_response.tex
Wording changes and adding my thoughts

@@
 We agree that the time scales we have explored are very short, but we are exploring a very particular scenario, and the delay times that we have chosen are not yet out of the realm of possibilities.
-\citet{Hirai15} quote the lower limit of a delay time to be $~10$ Myr, and that delay times of $~100$ Myr can explain the scatter in [Eu/Fe] for metal-poor stars in the galactic halo.
+\citet{Hirai15} quote the lower limit of a delay time to be $\sim10$ Myr, and that delay times of $\sim100$ Myr can explain the scatter in [Eu/Fe] for metal-poor stars in the galactic halo.
 
 \citet{Frebel23} also summarize the current state of discussion around the merger times for NSMs.
-They quote the minimum delay time to be between 10-100 Myr based on work done by other authors, and that there is some discussion that even shorter delay times of about 1 Myr could be possible.
+They quote the minimum delay time to be between 10--100 Myr based on work done by other authors, and that there is some discussion that even shorter delay times of about 1 Myr could be possible.
 
 For Reticulum II (Ret II) in particular, a long delay time of a couple Gyr is not compatible with the r-process enhanced stars.
-\citet{Simon23} provide an explanation for the timing requirements for r-process enrichment in Ret II, and they find that a NSM must occur with 500 Myr in order to reproduce the abundances and allow for thorough mixing.
+\citet{Simon23} provide an explanation for the timing requirements for r-process enrichment in Ret II, and they find that a NSM must occur within 500 Myr in order to reproduce the abundances and allow for thorough mixing.
 This requires the NSM to occur well before the formation of second generation stars.
@@
 Enzo does not have the capability to follow binary system formation.
-We simply do not have the resolution to accomplish such a task.
-Because of this, our NSM is an extremely ideal scenario, where we do not have to pick binary system parameters.
-The question of how this binary system formed in the first place is outside of the scope of this paper and would require significant contributions to the code base in order for that to happen in our simulations.
-We are simply assuming that there could exist a possibility where this type of binary system could form and then go on to merge together.
+We simply do not have the resolution to accomplish such a task in a cosmological setting.
+Because of this, our NSM model is an extremely ideal scenario, where we do not have to pick binary system parameters.
+The question of how this binary system formed in the first place is outside of the scope of this paper and would require significant modifications to the code base in order for that to happen in our simulations.
+We are assuming that there could exist a possibility where this type of binary system could form and then go on to merge together.
 Based on work cited above, we are comfortable with the delay times we have chosen, and they could add further information about the possibility of these short time delays moving forward.
@@
 We are operating under the assumption that if a NSM did occur in a galaxy like Ret II, then it would have to happen fairly early in order to allow for enough time to pass for thorough mixing to take place.
-We would also like to remind the referee that this is a "proof-of-concept" test of our model to see how the NSM may affect the second generation of stars.
-We aren't trying to exactly reproduce Ret II, but we want to begin to understand what the effects of a NSM of this type would look like early in the history of a galaxy.
+We would also like to remind the referee that this is a ``proof-of-concept'' test of our model to investigate how the NSM may affect the second generation of stars.
+We are not trying to exactly reproduce Ret II, but we want to begin to understand what are the effects of a NSM of this type early in the history of a galaxy.
 We would like to let the referee know that there is a follow up plan to this simulation, with more papers to come.
@@
 We were interested in the possibility of the NSM occurring early enough in the history of the galaxy to be a descendant of Pop III stars.
-We ask this question near the end of the Introduction: "...
-what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?" This is the question that we are exploring in this work.
+We ask this question near the end of the Introduction: ``...
+what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?'' This is the question that we are exploring in this work.
 
-We do not consider any binary system formation for Pop II stars in this work, mainly because Enzo does not currently have the capability to model binary systems for these stars.
-To keep things simple, we are only considering the binary system formation, and subsequent merging, of the NSs.
+We do not consider any binary system formation for Pop II stars in this work to isolate the effects from a NSM from a Pop III system alone.
+We are thus only considering the binary system formation, and subsequent merging, of the NSs.
 This would be an interesting thing to explore in the future however.
@@
 So we cannot pick apart the impacts of NSM on the physical properties of the first galaxies with Pop II star formation -- this was not something that we were trying to address really at all?
+    \item \jhw{I agree that the primary focus is the r-process enhancement and not the energetics.
+This is especially true because they will happen later in the halo's evolution when the mass is greater and potential is deeper, making its effect lesser than Pop III feedback and then Pop II feedback that has a large effect primarily due to the larger amount of stars that form.
+You can take the Pop III stellar masses from our 2020 paper and estimate the amount of energy released in radiation and SNe and show that it's much greater than a kilonova.
+This would be a useful comparison to add to the discussion.}
 \end{itemize}
@@
     \item Yes, this is a good question and one that I thought we made pretty clear.
-The answer to this is "I don't know".
+The answer to this is ``I don't know''.
 There are a lot of details to pick through in these simulations, and making comparisons across the simulations is a complicated task.
@@
 In this paper, we are simply reporting on the results.
+    \item \jhw{Yes, we should tell the referee that the causes of these diffenences are difficult to determine and that we will defer to a deeper study to a later paper because this paper primarily focuses on the enrichment.}
     \item We did find that NSM runs have higher cold gas mass fractions at late times. This could be one possible explanation for this.
@@
 We apologize for this, the caption was correct, but the label in the plot was wrong.
-The label should have read "Total Metallicity Fraction" instead of "P3 Metallicity Fraction".
+The label should have read ``Total Metallicity Fraction'' instead of ``P3 Metallicity Fraction''.
 The total metallicity is the metallicity of the stars from both Pop II and Pop III sources.
@@
 We apologize for that confusion.
-"Hyp." stood for "hypernova" which is how the original Pop III star ends its life.
-To keep things simple, we have changed that in the plots to say "OG" to make it clear that those lines correspond to the original run with no NSM.
+``Hyp.'' stood for ``hypernova'' which is how the original Pop III star ends its life.
+To keep things simple, we have changed that in the plots to say ``OG'' to make it clear that those lines correspond to the original run with no NSM.
+\jhw{Did you refer to the OG simulation as the original run in the caption?
+We should explicitly state this for non-native speakers and boomers.}
 
@@
 For example, at z = 10, they see $10^3 - 10^5 M_\odot$ for Pop II stars and $10^1 - 10^2 M_\odot$ for Pop III stars.
-For us, at z = 10 we see a few $\times 10^4 M_\odot$ for Pop II stars (which aligns with their results), and $~10^{3} M_{\odot}$ for Pop III stars, which is certainly larger than Riaz+22.
-However, they do give some generous ranges for the Pop II and Pop III stellar masses, so our results don't seem to be completely different from what they are saying.
+In our simulations at $z = 10$, we see a few$\times 10^4 M_\odot$ for Pop II stars, consistent with their results, and $\sim10^{3} M_{\odot}$ for Pop III stars, which is certainly larger than Riaz+22.
+However, they do give some generous ranges for the Pop II and Pop III stellar masses, so our results are not incompatible with Riaz+22.
         \item Re. Figure 3: This figure is very similar to the one from Yajima+23. We do see similar ratios overall (see Figure \ref{fig:ratio} above).
@@
 We have slightly lower values compared to Yajima.
-For all variation runs, for a stellar mass of $~10^{4.5} M_\odot$, we see a Pop III mass ratio of about $~10^{-1.5}$, as compared to Yajima's results of $~10^{-1}$.
-They have considerable scatter for their z = 10, 11, and 12 data.
+For all variation runs, for a stellar mass of $\sim10^{4.5} M_\odot$, we see a Pop III mass ratio of about $\sim10^{-1.5}$, as compared to Yajima's results of $\sim10^{-1}$.
+They have considerable scatter for their $z = 10$, 11, and 12 data.
 Certainly we see the same trend as them, as stellar mass increases, the ratio of Pop III stellar mass to total stellar mass decreases.
-We do see similar values at our maximum stellar mass value of $~10^{5.5} M_\odot$ having a mass ratio of $~10^{-2.25}$.
+We do see similar values at our maximum stellar mass value of $\sim10^{5.5} M_\odot$ having a mass ratio of $\sim10^{-2.25}$.
 An important thing to consider in this comparison is the much higher halo mass of their main halos.
-They look at a halo that grows to $5 \times 10^{11} M_\odot$ by z = 9.5, whereas our halo gets to $~2 \times 10^{8} M_\odot$ at z = 10 (see Figure \ref{fig:ratio} above).
+They look at a halo that grows to $5 \times 10^{11} M_\odot$ by $z = 9.5$, whereas our halo gets to $\sim2 \times 10^{8} M_\odot$ at $z = 10$ (see Figure \ref{fig:ratio} above).
         \item Based on these results, we certainly agree with their third bullet point.

### 2023-09-13 NSM_Skinner_Wise/referee/referee_response.tex
Starting to respond to comments.

@@
 Because of this, our NSM model is an extremely ideal scenario, where we do not have to pick binary system parameters.
-The question of how this binary system formed in the first place is outside of the scope of this paper and would require significant modifications to the code base in order for that to happen in our simulations.
+The question of how this binary system formed in the first place is outside the scope of this paper and would require significant modifications to the code base in order for that to happen in our simulations.
 We are assuming that there could exist a possibility where this type of binary system could form and then go on to merge together.
@@
 We are not trying to exactly reproduce Ret II, but we want to begin to understand what are the effects of a NSM of this type early in the history of a galaxy.
-We would like to let the referee know that there is a follow up plan to this simulation, with more papers to come.
+We would like to let the referee know that there is a follow-up plan to this simulation, with more papers to come.
 
 \textbf{(DS to-do)} We have added this explanation to SECTION.
-
-\textbf{DS Notes:}
-
-https://arxiv.org/pdf/2212.00810.pdf
-\begin{itemize}
-    \item for reticulum II, longer delay times (~couple Gyr) are incompatible with r-process stars in Ret II
-    \item must merge within about 500 Myr for Ret II
-    \item there is uniformity among the r-process enriched stars, indicating that thorough mixing needs to take place before star formation can occur.
-To allow for enough time, the NSM has to happen relatively early in the star formation history of ret II
-\end{itemize}
-
-https://arxiv.org/pdf/2302.09188.pdf
-\begin{itemize}
-    \item minimum delay time of 10-100 Myr
-    \item there is some argument that merging could happen on the order of 1 Myr
-    \item still lots of debate around the specifics
-\end{itemize}
 
@@
 
+Thank you for this recommendation. We have rewritten some of the abstract to include numerical values.
+
 \textbf{DS Notes:}
@@
 \end{tcolorbox}
+
+We would like to clarify something in order to respond to this point.
+The primary focus of this paper is the r-process enhancement of Pop II stars due to a NSM.
+We are not explicitly focused on the physical properties of the first galaxies.
+The interesting thing about this scenario, is that if a NSM occurs early in the star formation history of a galaxy, the r-process material that is produced during the merging event can end up in the next generation of stars, like the stars in Ret II.
+This is precisely what we were investigating.
+We would like to be able to say something about how the NSM parameters correlate with different Pop II star formation characteristics, but given our small sample size, and the intrinsic randomness of star formation that makes the simulations so different from one another, we cannot say with certainty how the NSM model parameters might affect different trends we may see initially.
+This is the last bullet point in our conclusion.
+
+\textbf{(DS to-do)} We have emphasized the uniqueness of NSMs at this early point in galaxy formation in SECTION.
 
@@
 \end{tcolorbox}
+
+Thank you for this point.
+We agree that the question you pose is a good one.
+Why does the NSM lead to larger Pop II stellar masses?
+You are correct that this is a complicated question to answer.
+The cause of these differences is difficult to determine due to the nature of the simulations.
+We discuss this at the beginning of our Discussion section.
+To summarize briefly here, between simulations, stars will not necessarily form in the same places, at the same times, and with the same masses.
+Because of this, it is extremely difficult to trace the butterfly effect of where the differences between simulations really stem from.
+We must defer to a deeper study on these differences which will be submitted later.
+This paper primarily focuses on the r-process enrichment of material early in the star formation history of a galaxy.
 
@@
 \jhw{Did you refer to the OG simulation as the original run in the caption?
-We should explicitly state this for non-native speakers and boomers.}
+We should explicitly state this for non-native speakers and boomers.} (DS: Just updated the first caption including ``OG'' to say what that is!)
 
@@
 
+Thank you for this suggestion. You are correct that we see similar results!
+
+\textbf{(DS to-do:)} We are investigating the case where Pop III and Pop II stars coexist with one another for a brief period of time. 
 \textbf{DS Notes:}

### 2023-09-13 NSM_Skinner_Wise/referee/referee_response.tex
Cleaning up report.

@@
 
-\textbf{(DS to-do)} We have added this explanation to SECTION.
+We have added a brief explanation to the subsection ``Neutron star merger model and simulation suite''.
 
@@
 
-\textbf{(DS to-do)} We have made our motivation more clear in SECTION.
+We have added a clarifying sentence in the subsection ``Pop III and Pop II star formation and feedback'' to make it clear that we are not including Pop III and Pop II binary systems.
+We have also added language at the top of the subsection ``Neutron star merger model and simulation suite'' to make it clear about what we are studying.
 
@@
 Thank you for this recommendation. We have rewritten some of the abstract to include numerical values.
-
-\textbf{DS Notes:}
-Replace two general sentences with these more specific ones.
-\begin{itemize}
-    \item A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
-    \item When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.
-\end{itemize}
 
@@
 
-\textbf{(DS to-do)} We have emphasized the uniqueness of NSMs at this early point in galaxy formation in SECTION.
-
-\textbf{DS Notes:}
-\begin{itemize}
-    \item I feel like the main thing that makes NSM unique is their production of r-process elements (along with the effects of a kilonova, but maybe we don't mention that?).
-One of the main points is that NSMs can produce r-process enhanced stars, but also that the exact feedback mechanisms that occur appear to drastically affect results (last bullet point in conclusions).
-So we cannot pick apart the impacts of NSM on the physical properties of the first galaxies with Pop II star formation -- this was not something that we were trying to address really at all?
-    \item \jhw{I agree that the primary focus is the r-process enhancement and not the energetics.
-This is especially true because they will happen later in the halo's evolution when the mass is greater and potential is deeper, making its effect lesser than Pop III feedback and then Pop II feedback that has a large effect primarily due to the larger amount of stars that form.
-You can take the Pop III stellar masses from our 2020 paper and estimate the amount of energy released in radiation and SNe and show that it's much greater than a kilonova.
-This would be a useful comparison to add to the discussion.}
-\end{itemize}
+We have emphasized the uniqueness of NSMs at this early point in galaxy formation in the Introduction.
 
@@
 
-\textbf{DS Notes:}
-\begin{itemize}
-    \item Yes, this is a good question and one that I thought we made pretty clear.
-The answer to this is ``I don't know''.
-There are a lot of details to pick through in these simulations, and making comparisons across the simulations is a complicated task.
-Because we don't have a large sample size to study, it's hard to say anything conclusive about how the NSM might affect the Pop II stellar masses, and whether other star formation and feedback is affecting it as well.
-This is a question we are continuing to explore.
-In this paper, we are simply reporting on the results.
-    \item \jhw{Yes, we should tell the referee that the causes of these diffenences are difficult to determine and that we will defer to a deeper study to a later paper because this paper primarily focuses on the enrichment.}
-    \item We did find that NSM runs have higher cold gas mass fractions at late times. This could be one possible explanation for this.
-\end{itemize}
+We have included a sentence in the Discussion to alert the reader that studies are ongoing and a deeper study is required to answer these type of questions.
 
@@
 To keep things simple, we have changed that in the plots to say ``OG'' to make it clear that those lines correspond to the original run with no NSM.
-\jhw{Did you refer to the OG simulation as the original run in the caption?
-We should explicitly state this for non-native speakers and boomers.} (DS: Just updated the first caption including ``OG'' to say what that is!)
 
@@
 
-Thank you for this suggestion. You are correct that we see similar results!
+Thank you for this suggestion.
+You are correct that we see similar results!
+We have added this short comparison to the discussion section.
+We are leaving the figures we made to make the comparison in this report, but we are electing to not add more plots to the paper.
 
-\textbf{(DS to-do:)} We are investigating the case where Pop III and Pop II stars coexist with one another for a brief period of time. 
-\textbf{DS Notes:}
 \begin{figure}[h]
@@
 
-\begin{itemize}
-    \item Riaz+22: compare with their Figure 1 and 3 (https://iopscience.iop.org/article/10.3847/2041-8213/ac8ea6/meta)
-    \begin{itemize}
-        \item Re.
-Figure 1: Looking at the redshift range between 10 and 20, and comparing with their halo masses between $10^7 - 10^9 M_\odot$ since this is the closest out halo gets to by the end of the simulation, we do see much higher stellar masses compared to them.
-For example, at z = 10, they see $10^3 - 10^5 M_\odot$ for Pop II stars and $10^1 - 10^2 M_\odot$ for Pop III stars.
-In our simulations at $z = 10$, we see a few$\times 10^4 M_\odot$ for Pop II stars, consistent with their results, and $\sim10^{3} M_{\odot}$ for Pop III stars, which is certainly larger than Riaz+22.
-However, they do give some generous ranges for the Pop II and Pop III stellar masses, so our results are not incompatible with Riaz+22.
-        \item Re. Figure 3: This figure is very similar to the one from Yajima+23. We do see similar ratios overall (see Figure \ref{fig:ratio} above).
-    \end{itemize}
-    \item Yajima+23: compare with their Figure 4, third bullet point in their conclusion (https://arxiv.org/pdf/2211.12970.pdf)
-    \begin{itemize}
-        \item Re: Figure 4.
-I have made this same plot for our work.
-We have slightly lower values compared to Yajima.
-For all variation runs, for a stellar mass of $\sim10^{4.5} M_\odot$, we see a Pop III mass ratio of about $\sim10^{-1.5}$, as compared to Yajima's results of $\sim10^{-1}$.
-They have considerable scatter for their $z = 10$, 11, and 12 data.
-Certainly we see the same trend as them, as stellar mass increases, the ratio of Pop III stellar mass to total stellar mass decreases.
-We do see similar values at our maximum stellar mass value of $\sim10^{5.5} M_\odot$ having a mass ratio of $\sim10^{-2.25}$.
-An important thing to consider in this comparison is the much higher halo mass of their main halos.
-They look at a halo that grows to $5 \times 10^{11} M_\odot$ by $z = 9.5$, whereas our halo gets to $\sim2 \times 10^{8} M_\odot$ at $z = 10$ (see Figure \ref{fig:ratio} above).
-        \item Based on these results, we certainly agree with their third bullet point.
-In general, the mass fraction of Pop III stars is less than 0.01 for halos with stellar masses $> 10^{4} M_\odot$
-    \end{itemize}
-\end{itemize}
-
 We again thank the referee for the insightful review that helped

### 2023-09-13 NSM_Skinner_Wise/NSM_mixing.tex
Adjusting text to reflect referee report response.

@@
 In general, a NSM leads to a significant r-process enhancement in the second generation of stars.
-A high explosion energy leads to almost all enhanced r-process stars being highly enhanced, while a lower explosion energy leads to a higher mass fraction of stars being r-process enhanced, but not as many being highly enhanced.
-When a NSM has a short delay time, there is a higher mass fraction of stars being r-process enhanced, but a smaller mass fraction being highly enhanced compared to longer delay times.
-This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
+\textbf{A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
+When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
 \end{abstract}
@@
 Since this galaxy is so isolated, it serves as an ideal case study for simulating this scenario: namely, what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?
+\textbf{This type of scenario is particularly unique due to the chemical impact a NSM could have on the star formation history of a galaxy.
+If a NSM did occur early in the history of Ret II, the r-process enriched stars are a special and direct connection to previous generations of stars.}
 
@@
 \subsection{Neutron star merger model and simulation suite} \label{sec:NSM_model}
-We implement a new NSM model within \enzo{} to control the delay time and the explosion energy of the event, modelled as a single star particle.
+\textbf{To explore how a NSM descendent from Pop III stars affects the r-process enrichment of Pop II stars, w}e implement a new NSM model within \enzo{} to control the delay time and the explosion energy of the event, modelled as a single star particle.
 Upon completion of the original simulation, a single Pop III star is chosen as the candidate NSM event.
@@
 For this proof of concept, the total ejecta mass is set to $0.01 \Ms$, but in practice, due to the Cartesian discretization of a sphere in of Enzo, the actual mass ejected is $0.0169 M_{\odot}$.
+\textbf{The delay times chosen for these runs are on the shorter end of timescales for the merging of two NSs to take place, but for this proof of concept, we wanted to explore this particular situation where a NSM occurs early in the star formation history of the galaxy.
+For a galaxy like Ret II, a NSM would have had to occur within 500 Myr to allow for ample time for thorough mixing to take place within the halo \citep{Simon23}.
+Delay times of 10, 100, and 300 Myr are short, but are not completely out of the realm of possibilities, and allow us to see how a NSM affects subsequent star formation at this early point in time.}
 
@@
 Rather, the total Pop II stellar mass is the indicator that will be presented throughout this work.
+\textbf{We do not take into account the effects of Pop III or Pop II binary systems due to the limiting resolution of our simulations.}
 
@@
 	\includegraphics[width=\columnwidth]{plots/eng_stellar_dist.pdf}
-	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original run.
+	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original \textbf{(OG)} run.
 The dashed lines indicate the half-mass radius, which are 331.2 pc, 37.1 pc, 65.3 pc, and 50.6 pc for the original run, run D, run Fiducial, and run E, respectively.
@@
 \end{figure}
+
+\textbf{}
 
@@
 
+\textbf{For all runs, we see similar Pop III stellar masses as compared to some recent studies.
+\citet{Riaz22} studied the Pop III contribution to high redshift galaxies for a range of halo masses.
+They find that a halo with a mass of $10^7$ \Ms has a Pop III mass fraction of $\sim 10^{-1}$ at $z \approx 12$.
+For our runs, at a similar time and halo mass, we also see a Pop III mass fraction of $\sim 10^{-1}$.
+By $z = 10$, we see $\sim 10^{4}$ \Ms of Pop II stars and $\sim 10^{3}$ \Ms for Pop III stars, as compared to $10^3 - 10^5$ \Ms of Pop II stars and  $10^1 - 10^2$ \Ms of Pop III stars found by \citet{Riaz22}.
+While we do see a slightly higher value of Pop III stellar masses as compared to them, our overall mass fractions are similar.
+\citet{Yajima23} studied the first galaxies and their Pop III contributions in order to compare with results from JWST.
+They also look at the Pop III mass fraction (see their Figure 5) as compared to the total stellar mass.
+They report a much broader range of values for different redshifts in general.
+For a stellar mass of $10^{4.5}$ \Ms, they find a Pop III mass fraction of $\sim 10^{-0.75}$, while we see a mass fraction for that stellar mass closer to $10^{-1.5}$ \Ms.
+However, we do see a similar trend, that as stellar mass increases, the Pop III mass fraction begins to decrease.
+At the end of our simulations when our halo has a stellar mass of $\sim 10^{5.5}$ \Ms, we see a Pop III mass fraction of $\sim 10^{-2.25}$, which is similar to \citet{Yajima23}.
+Based on these results, we agree with their conclusion that for halos with stellar masses of $\sim 10^{7}$ \Ms, the Pop III mass fraction is small, at $< 0.01$ }
+
 This work represents some of the first simulations on the chemical and dynamical impacts of a NSM, with various parameters, in a cosmological setting, and thus there are some difficulties that come with this kind of study.
@@
 We stress that this is merely a proof-of-concept study to show that we can study the impacts of NSMs in a cosmological setting to present meaningful results that can enhance our understanding of r-process enrichment in the early universe.
+\textbf{Studies are currently underway to try to separate the source of differences between the simulations, and are outside the scope of this paper.}
 

### 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
Minor changes to new text

@@
 We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time.
-In general, a NSM leads to a significant r-process enhancement in the second generation of stars.
-\textbf{A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
+In general, a NSM leads to a significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.
+A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
 When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
@@
 For this proof of concept, the total ejecta mass is set to $0.01 \Ms$, but in practice, due to the Cartesian discretization of a sphere in of Enzo, the actual mass ejected is $0.0169 M_{\odot}$.
-\textbf{The delay times chosen for these runs are on the shorter end of timescales for the merging of two NSs to take place, but for this proof of concept, we wanted to explore this particular situation where a NSM occurs early in the star formation history of the galaxy.
+\textbf{The delay times chosen for these runs are on the shorter end of timescales for the merging of two NSs to take place, but for this proof of concept, we explore this particular situation where a NSM occurs early in the star formation history of the galaxy.
 For a galaxy like Ret II, a NSM would have had to occur within 500 Myr to allow for ample time for thorough mixing to take place within the halo \citep{Simon23}.
@@
 \citet{Riaz22} studied the Pop III contribution to high redshift galaxies for a range of halo masses.
-They find that a halo with a mass of $10^7$ \Ms has a Pop III mass fraction of $\sim 10^{-1}$ at $z \approx 12$.
-For our runs, at a similar time and halo mass, we also see a Pop III mass fraction of $\sim 10^{-1}$.
-By $z = 10$, we see $\sim 10^{4}$ \Ms of Pop II stars and $\sim 10^{3}$ \Ms for Pop III stars, as compared to $10^3 - 10^5$ \Ms of Pop II stars and  $10^1 - 10^2$ \Ms of Pop III stars found by \citet{Riaz22}.
+They find that a halo with a mass of $10^7$ \Ms{} has a Pop III mass fraction of $\sim 0.1$ at $z \approx 12$.
+For our runs, at a similar time and halo mass, we also see a Pop III mass fraction of $\sim 0.1$.
+By $z = 10$, we see $\sim 10^{4}$ \Ms{} of Pop II stars and $\sim 10^{3}$ \Ms{} for Pop III stars, as compared to $10^3 - 10^5$ \Ms{} of Pop II stars and  $10^1 - 10^2$ \Ms{} of Pop III stars found by \citet{Riaz22}.
 While we do see a slightly higher value of Pop III stellar masses as compared to them, our overall mass fractions are similar.
@@
 They report a much broader range of values for different redshifts in general.
-For a stellar mass of $10^{4.5}$ \Ms, they find a Pop III mass fraction of $\sim 10^{-0.75}$, while we see a mass fraction for that stellar mass closer to $10^{-1.5}$ \Ms.
+For a stellar mass of $10^{4.5}$ \Ms, they find a Pop III mass fraction of $\sim 0.18$, while we see a mass fraction for that stellar mass around 0.03.
 However, we do see a similar trend, that as stellar mass increases, the Pop III mass fraction begins to decrease.
-At the end of our simulations when our halo has a stellar mass of $\sim 10^{5.5}$ \Ms, we see a Pop III mass fraction of $\sim 10^{-2.25}$, which is similar to \citet{Yajima23}.
+At the end of our simulations when our halo has a stellar mass of $\sim 10^{5.5}$ \Ms, we find a Pop III mass fraction of $\sim 0.006$, which is similar to \citet{Yajima23}.
 Based on these results, we agree with their conclusion that for halos with stellar masses of $\sim 10^{7}$ \Ms, the Pop III mass fraction is small, at $< 0.01$ }
@@
 We stress that this is merely a proof-of-concept study to show that we can study the impacts of NSMs in a cosmological setting to present meaningful results that can enhance our understanding of r-process enrichment in the early universe.
-\textbf{Studies are currently underway to try to separate the source of differences between the simulations, and are outside the scope of this paper.}
+\textbf{We plan to follow up this paper with a study that separates the source of differences between the simulations, and are outside the scope of this paper.}
 

### 2023-09-14 NSM_Skinner_Wise/referee/referee_response.tex
Small adjustment.
Adding energy comparison

@@
 addressed their points individually below.  In the manuscript, we have
-boldfaced the added text and crossed out the deleted text.
+boldfaced the added text.
 
@@
 This is the last bullet point in our conclusion.
+
+The NSM alone should also not have a large dynamical effect on the galaxy.
+In these early times, when Pop III stars are also forming, they will be the dominant source of energy in the galaxy.
+We can make an order of magnitude estimate of this.
+If we consider just the hydrogen ionizing radiation coming from Pop III stars, for a Pop III stellar mass of $10^3$ \Ms, and using the ionizing rates and energies from \citet{Schaerer03}, we find that the hydrogen ionizing stellar energy is $\sim 10^{54}$ erg.
+About 1\% of this is converted into thermal and kinetic energy, and if we assume that we get about 1 SN per 100 from a Salpeter IMF, we get $\sim 10^{52}$ erg from SNe.
+The kilonova produced by GW170817 resulted in about $10^{51}$ erg of ejecta energy \citep{Metzger19}.
+We can see that the energetic effect from Pop III stars is much larger compared to the effects from the kilonova.
 

### 2023-09-14 NSM_Skinner_Wise/referee/referee_response.tex
Adding citation for 1000 Msun choice

@@
 We can make an order of magnitude estimate of this.
-If we consider just the hydrogen ionizing radiation coming from Pop III stars, for a Pop III stellar mass of $10^3$ \Ms, and using the ionizing rates and energies from \citet{Schaerer03}, we find that the hydrogen ionizing stellar energy is $\sim 10^{54}$ erg.
+If we consider just the hydrogen ionizing radiation coming from Pop III stars, for a Pop III stellar mass of $10^3$ \Ms{} that is approximately the mean we found in \citep{Skinner20}, and using the ionizing rates and energies from \citet{Schaerer03}, we find that the hydrogen ionizing stellar energy is $\sim 10^{54}$ erg.
 About 1\% of this is converted into thermal and kinetic energy, and if we assume that we get about 1 SN per 100 from a Salpeter IMF, we get $\sim 10^{52}$ erg from SNe.
@@
     \centering
-    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_stellar_mass.pdf} }}%
+    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_stpellar_mass.pdf} }}%
     \qquad

### 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
Moving around OG definition.

@@
 	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
-	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original run.
+	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original \textbf{(OG)} run.
 The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.
@@
 	\includegraphics[width=\columnwidth]{plots/eng_stellar_dist.pdf}
-	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original \textbf{(OG)} run.
+	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original run.
 The dashed lines indicate the half-mass radius, which are 331.2 pc, 37.1 pc, 65.3 pc, and 50.6 pc for the original run, run D, run Fiducial, and run E, respectively.

### 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
Bringing abstract to word limit. Resubmitting.

@@
 \begin{abstract}
-	The exact evolution of elements in the universe, from primordial hydrogen and helium to heavier elements like gold and platinum produced via the r-process, is still under scrutiny.
-The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants.
-These remnants can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to occur.
-In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances.
+	The exact evolution of elements in the universe, from primordial to heavier elements produced via the r-process, is still under scrutiny.
+The supernova deaths of the very first stars led to the enrichment of their local environments, and can leave behind neutron stars (NS) as remnants.
+These remnants can end up in binary systems with other NSs, and eventually merge, allowing for the r-process to occur.
+We study the scenario where a single NS merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances.
 We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time.
-In general, a NSM leads to a significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.
-A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced.
-When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
+In general, a NSM leads to significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.
+A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to 80\% being enhanced, but only 14\% being highly enhanced.
+When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly enhanced, while 64\% is highly enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
 \end{abstract}

### 2023-09-15 NSM_Skinner_Wise_arxiv/NSM_mixing.tex
Making new directory for arxiv, to keep arxiv version and referee version separate.

--- 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
@@
 We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time.
-In general, a NSM leads to significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.
+In general, a NSM leads to significant r-process enhancement in the second generation of stars in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.
 A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to 80\% being enhanced, but only 14\% being highly enhanced.
-When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly enhanced, while 64\% is highly enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
+When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly enhanced, while 64\% is highly enhanced for the longest delay time of 100 Myr.
+This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
 \end{abstract}
@@
 Since this galaxy is so isolated, it serves as an ideal case study for simulating this scenario: namely, what happens if a single NSM, produced from the remnants of Pop III stars, occurs within a galaxy in the early universe?
-\textbf{This type of scenario is particularly unique due to the chemical impact a NSM could have on the star formation history of a galaxy.
-If a NSM did occur early in the history of Ret II, the r-process enriched stars are a special and direct connection to previous generations of stars.}
+This type of scenario is particularly unique due to the chemical impact a NSM could have on the star formation history of a galaxy.
+If a NSM did occur early in the history of Ret II, the r-process enriched stars are a special and direct connection to previous generations of stars.
 
@@
 \subsection{Neutron star merger model and simulation suite} \label{sec:NSM_model}
-\textbf{To explore how a NSM descendent from Pop III stars affects the r-process enrichment of Pop II stars, w}e implement a new NSM model within \enzo{} to control the delay time and the explosion energy of the event, modelled as a single star particle.
+To explore how a NSM descendent from Pop III stars affects the r-process enrichment of Pop II stars, we implement a new NSM model within \enzo{} to control the delay time and the explosion energy of the event, modelled as a single star particle.
 Upon completion of the original simulation, a single Pop III star is chosen as the candidate NSM event.
@@
 For this proof of concept, the total ejecta mass is set to $0.01 \Ms$, but in practice, due to the Cartesian discretization of a sphere in of Enzo, the actual mass ejected is $0.0169 M_{\odot}$.
-\textbf{The delay times chosen for these runs are on the shorter end of timescales for the merging of two NSs to take place, but for this proof of concept, we explore this particular situation where a NSM occurs early in the star formation history of the galaxy.
+The delay times chosen for these runs are on the shorter end of timescales for the merging of two NSs to take place, but for this proof of concept, we explore this particular situation where a NSM occurs early in the star formation history of the galaxy.
 For a galaxy like Ret II, a NSM would have had to occur within 500 Myr to allow for ample time for thorough mixing to take place within the halo \citep{Simon23}.
-Delay times of 10, 100, and 300 Myr are short, but are not completely out of the realm of possibilities, and allow us to see how a NSM affects subsequent star formation at this early point in time.}
+Delay times of 10, 100, and 300 Myr are short, but are not completely out of the realm of possibilities, and allow us to see how a NSM affects subsequent star formation at this early point in time.
 
@@
 Rather, the total Pop II stellar mass is the indicator that will be presented throughout this work.
-\textbf{We do not take into account the effects of Pop III or Pop II binary systems due to the limiting resolution of our simulations.}
+We do not take into account the effects of Pop III or Pop II binary systems due to the limiting resolution of our simulations.
 
@@
 
-\subsection{Evolution of the main halo \textbf{in the original run}} \label{sec:main_halo}
+\subsection{Evolution of the main halo in the original run} \label{sec:main_halo}
 \begin{figure} 
@@
 
-\textbf{In the original run with no NSM,} the most massive progenitor of the main halo is first identified at $z = 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
+In the original run with no NSM, the most massive progenitor of the main halo is first identified at $z = 26.9$ with a mass of $10^{4.6} \Ms$, and ends with a mass of $10^{8.19} \Ms$ at $z = 10$.
 During that time, the halo forms two Pop III stars with masses of 26.5 \Ms{} and 195.5 \Ms{} at 150.7 Myr ($z = 22.6$) and 286.1 Myr ($z = 14.4$), respectively.
@@
 	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
-	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original \textbf{(OG)} run.
+	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original (OG) run.
 The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass.
@@
 \end{figure}
-
-\textbf{}
 
@@
 
-\textbf{For all runs, we see similar Pop III stellar masses as compared to some recent studies.
+For all runs, we see similar Pop III stellar masses as compared to some recent studies.
 \citet{Riaz22} studied the Pop III contribution to high redshift galaxies for a range of halo masses.
@@
 At the end of our simulations when our halo has a stellar mass of $\sim 10^{5.5}$ \Ms, we find a Pop III mass fraction of $\sim 0.006$, which is similar to \citet{Yajima23}.
-Based on these results, we agree with their conclusion that for halos with stellar masses of $\sim 10^{7}$ \Ms, the Pop III mass fraction is small, at $< 0.01$ }
+Based on these results, we agree with their conclusion that for halos with stellar masses of $\sim 10^{7}$ \Ms, the Pop III mass fraction is small, at $< 0.01$.
 
@@
 We stress that this is merely a proof-of-concept study to show that we can study the impacts of NSMs in a cosmological setting to present meaningful results that can enhance our understanding of r-process enrichment in the early universe.
-\textbf{We plan to follow up this paper with a study that separates the source of differences between the simulations, and are outside the scope of this paper.}
+We plan to follow up this paper with a study that separates the source of differences between the simulations, and are outside the scope of this paper.
 

### 2023-10-23 referee2/referee_response.tex
Adding second referee report to referee2

\documentclass[11pt]{article}
%\renewcommand\refname{ }

\usepackage{fullpage}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{listings,color}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage{natbib}
\usepackage{subfig}

\input macros.tex

\begin{document}

\begin{center} 
\bfseries{
\begin{large}
  Response to referee report for manuscript ref. MN-23-2721-MJ.R1
\end{large}
}
\end{center}

\begin{tcolorbox}[colback={lightgray}]
The authors have revised the manuscript based on some of my comments. The current version is better than the previous one. However, important points which I requested in the report have not been addressed well.
\end{tcolorbox}

We thank the referee for returning comments back to us. We will address the issues below and have boldfaced any changes made to the manuscript.

\begin{tcolorbox}[colback={lightgray}]
1) For now, there is no evidence that neutron stars originated from Population III stars occurred within 100 Myr. In my previous report, I requested the authors to add information about the binary systems to induce the neutron star mergers within a very short time scale. Merely referring to Simon et al. (2023) is insufficient. Modeling the star formation history based on the color-magnitude diagram involves a large error, which cannot be evidence of the neutron star merger originated from Population III stars with the short time scale. Also, they just suggested r-process occurred within 500 Myr in which a lot of Population II stars can form and its stellar mass can be much larger than Population III stars. I understand some previous models considered the merger parameters extended to the short time scale. However, they did not provide a strong constraint in which Pop III neutron stars must merge within < 100 Myr. In dense star clusters, the angular momentum of binary systems can be lost via three-body interaction, leading to mergers within a short time scale. On the other hand, the short-time scale merger of a pure binary system sounds very difficult. I would like to request that the authors will explain what kind of binary systems can induce the NS-NS merger within 10-100 Myr and how frequently such binary systems are likely to form.
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}]   
    The authors consider the NS-NS mergers originated only from Population III stars. I understand the authors investigate an ideal case. However, the motivation of this work is to understand the origin of r-process enhanced stars in nearby dwarf galaxies. In considering the long-time history of galaxies, we cannot avoid the contribution from Population I/II stars. The authors should discuss this more carefully. Are there any possibilities that we can observe evidence of the metal enrichment solely from Population III stars? Simon et al (2023) indicated that 80% of stars formed in the early Universe. Therefore, if it is true, stars of approximately 3000 solar masses were formed in that era. Is the contribution from Population III stars significant?
\end{tcolorbox}

\begin{tcolorbox}[colback={lightgray}] 
Ret II should be written after showing the formal name, “Reticulum II”.
\end{tcolorbox}

We again thank the referee for the insightful review that helped improve our paper.

\bibliographystyle{plainnat}
\bibliography{drenniks}

\end{document}

### 2023-10-27 referee2/referee_response.tex
Adding my thoughts on the 2nd report

@@
 \usepackage{subfig}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks,
+    citecolor=blue,
+    filecolor=black,
+    linkcolor=blue,
+    urlcolor=blue
+}
+\usepackage{url}
 
@@
 I understand some previous models considered the merger parameters extended to the short time scale.
-However, they did not provide a strong constraint in which Pop III neutron stars must merge within < 100 Myr.
+However, they did not provide a strong constraint in which Pop III neutron stars must merge within $<$100 Myr.
 In dense star clusters, the angular momentum of binary systems can be lost via three-body interaction, leading to mergers within a short time scale.
@@
 \end{tcolorbox}
+
+\noindent\textbf{JHW notes}
+\begin{itemize}
+  \item The intro of \href{https://ui.adsabs.harvard.edu/abs/2019ApJ...878L..12S/abstract}{Safarzadeh \& Berger (2019)} has some good information about constraining the minimum merger time.
+The merger time distribution can be modeled as a power-law $dN/dt_{\rm merge} \propto t^\Gamma$, where $\Gamma$ is between --1.5 and --1.
+This comes from the initial binary separation distribution, which is steeper if the binary goes through a common envelope phase, meaning that there will be more close binaries in this case.
+  \item Also see \href{https://arxiv.org/abs/1812.10065}{Belczynski et al.
+(2018)}, especially their Figures 7--10.
+There aren't many delay times below 100 Myr, but it's non-zero.
+In this paper, they define the delay time, starting at the stellar binary formation, not the NS formation.
+The stellar lifetimes set the minimum value ($\sim 10$ Myr) in their delay time distributions.
+Reading Section 4.1, the models with lower minimum times have small (models NN1, NN6) or zero (model NN13) NS natal kicks after the NS is formed.
+This paper states that these are extreme assumptions that require a very high common envelope efficiency, but go with them for comparison.
+I'm not sure whether this paper was even published, but we can still cite it.
+  \item I would look for more references on the minimum time constraints, not just about Ret II.
+But we could argue that in particular cases where there has been a common envelope phase, one would except the resulting NS binary to have a small separation and thus merger time.
+Also I would look in the papers that we've referenced so far to see whether the delay time is defined as the time between SF $\rightarrow$ NSM or NS formation $\rightarrow$ NSM.
+This only adds 10-20 Myr to the delay time, but it would make our 10 Myr delay times more reasonable.
+\end{itemize}
 
@@
 Are there any possibilities that we can observe evidence of the metal enrichment solely from Population III stars?
-Simon et al (2023) indicated that 80% of stars formed in the early Universe.
+Simon et al (2023) indicated that 80\% of stars formed in the early Universe.
 Therefore, if it is true, stars of approximately 3000 solar masses were formed in that era.
@@
 \end{tcolorbox}
+
+\noindent\textbf{JHW notes}
+\begin{itemize}
+  \item This is a fair point.
+The only stars that will be solely enriched by Pop III stars would be the second generation of stars whose birth gas hasn't been enriched by metal-enriched stars.
+This would be the initial starburst of the galaxy, which should be extremely metal-poor $[Z/H] \sim -3$  Of those 80\% of the star formation in the early universe, we could use some star formation histories from the Birth of a Galaxy simulations to determine what fraction form in the initial burst.
+\end{itemize}
 

### 2023-10-31 referee2/referee_response.tex
Adding notes

@@
 
+\noindent\textbf{DS notes}
+\begin{itemize}
+  \item \href{https://iopscience.iop.org/article/10.1088/0004-637X/759/1/52/pdf}{Dominik et al.
+2015}: Figure 8 shows delay time distributions.
+They have delay time defined as "the sum of the time needed to form two compact objects from a ZAMS binary and the time for the two compact objects to coalesce due to the emission of gravitational radiation".
+They say that the latter half of the time, when the inspiral takes place, is typically ~Gyr and that's what they find for their average.
+There are some models that have delay times of about 10 Myr.
+  \item \href{https://iopscience.iop.org/article/10.1086/319641/pdf}{Belczynski et al.
+2001}: They look at a different formation channel for NS binary systems, where a close binary neutron star system forms out of neutron stars that are not recycled (neither has been recycled by accretion).
+The merger times of these systems are on the lower end of $10^4$ - $10^8$ yr.
+  \item \href{https://www.aanda.org/articles/aa/pdf/2016/05/aa28193-16.pdf}{Mennekens et al.
+2016}: Their delay time is defined as the time between the formation of the binary system and the eventual formation of a NS-NS binary system plus the merger time.
+  \item \href{https://arxiv.org/pdf/2106.13383.pdf}{Jeon et al.
+2019}: They run zoom-in simulations studying the origin of MP r-II stars in UFDs.
+They assume that the merger occurs 5 Myr after the binary neutron star system forms, corresponding to the fast-merging channel.
+  \item Simon et al. 2023: They define the delay time as the time between the formation of the first stars and r-process nucleosynthesis and find for Ret II, it must be less than 500 Myr.
+  \item The referee is really focused on neutron stars from Pop III stars.
+From what I've seen, there isn't a lot of work on neutron stars from Pop III stars and what the formation of those systems looked like.
+Based on some of the work we have both cited, it seems as if there is a fast-formation channel for neutron stars if they have low natal kicks and undergo a common envelope phase.
+Our response here may be along the lines of "it is possible (low natal-kicks, common envelope phase), but it is likely very rare" and we can cite some merger rates from Belczynski if they provide any.
+\end{itemize}
+
 \begin{tcolorbox}[colback={lightgray}]   
@@
 
+\noindent\textbf{DS notes}
+\begin{itemize}
+  \item I see this point, but I am also thinking that we could revise some of our wording to say that we are only focused on the r-process enrichment from neutron star mergers.
+In that sense, we are seeing the "lower bound" of r-process enrichment for this type of system.
+  \item And are you talking about finding what fraction of the total amount of stars form in our galaxy in the initial burst? 
+  \item Also, it's not like we aren't considering metal enrichment form Pop III and Pop II stars, we just don't call the metallicity fraction enriched by those stars "r-process". 
+\end{itemize}
+
 \begin{tcolorbox}[colback={lightgray}] 

### 2023-12-07 referee2/referee_response.tex
Adding imf notebook and more thoughts

@@
 
+\noindent\textbf{JHW note (07 Dec 2023)}
+
+I agree that we should add a sentence or two at the end of the next to last paragraph in Section 2.2, saying that a short delay time is possible yet rare if the system has a low natal kick and undergoes a common envelope phase, and cite those works.
+I really hope that the referee is appeased by this.
+
 \begin{tcolorbox}[colback={lightgray}]   
@@
 The only stars that will be solely enriched by Pop III stars would be the second generation of stars whose birth gas hasn't been enriched by metal-enriched stars.
-This would be the initial starburst of the galaxy, which should be extremely metal-poor $[Z/H] \sim -3$  Of those 80\% of the star formation in the early universe, we could use some star formation histories from the Birth of a Galaxy simulations to determine what fraction form in the initial burst.
+This would be the initial starburst of the galaxy, which should be extremely metal-poor $[Z/H] \sim -3$.
+Of those 80\% of the star formation in the early universe, we could use some star formation histories from the Birth of a Galaxy simulations to determine what fraction form in the initial burst.
 \end{itemize}
 
-\noindent\textbf{DS notes}
+\noindent\textbf{DS notes {(\color{purple} JHW responses})}
 \begin{itemize}
@@
 In that sense, we are seeing the "lower bound" of r-process enrichment for this type of system.
+  \item {\color{purple} Agreed that this can be addressed by some rewording, saying that we aren't focused on the complete r-process enrichment history, but only the beginning, providing a lower limit.}
   \item And are you talking about finding what fraction of the total amount of stars form in our galaxy in the initial burst? 
+  \item {\color{purple} I thought about this some more, and I don't think we should discuss the stellar mass formed in the early Universe because the galaxy hasn't stopped forming stars.
+The initial burst (looks like a single star particle with $M \simeq 10^3 M_\odot$) wouldn't be the right value to use because it's shortly after Pop III forms at $t \sim 200$ Myr and is not r-process enhanced.
+Also, the final mass wouldn't be valid either because the stars forming at late times could be r-enhanced by Pop II stars.}
+  \item {\color{purple} But as a discussion point, we could use that 3000\Ms value given by the referee and convert it into a stellar mass at these redshifts.
+I've pushed a Jupyter notebook that calculates what fraction of these stars would still be alive today, and it's $\sim$40\%.
+So the star formation event that formed those 3000\Ms low-mass stars is 7500\Ms, which is right in the middle of our stellar masses.
+This is a little hand wavy, but I think it's good to point out.}
   \item Also, it's not like we aren't considering metal enrichment form Pop III and Pop II stars, we just don't call the metallicity fraction enriched by those stars "r-process".
+  \item {\color{purple} Exactly.  I think we should emphasize this fact in the response, but I don't think we need to add anything to the paper about it.}
 \end{itemize}

### 2024-01-01 referee2/referee_response.tex
Referee response -- just need final approval

@@
 
-We thank the referee for returning comments back to us. We will address the issues below and have boldfaced any changes made to the manuscript.
+We thank the referee for returning comments back to us.
+We will address the issues below and have \textbf{boldfaced} and \textit{italicized} any changes made to the manuscript to differentiate from the changes made to the manuscript in the first revision cycle.
 
@@
 
+\noindent\textbf{DS note (01 Jan 2024)}
+Below is my response to the referee -- feel free to edit:
+
+It is true that there is limited evidence that neutron stars originating from Pop III stars can merge within 100 Myr.
+This is clearly a field that will require much more investigation as we continue to probe to earlier and earlier times.
+However, some studies have investigated these short delay time scenarios.
+\citet{Belczynski18} study binary neutron star system formation and found that their models with lower minimum times have small or zero neutron star natal kicks, and thus undergo a highly efficient common envelope phase.
+This corresponds to a fast-formation channel for neutron star binary systems, and could possibly lead to shorter delay times.
+\citet{Jeon21} also investigate the origin of r-process enhanced stars in ultra-faint dwarf galaxies and agree that the exact origin of these NSMs is unknown, and likely very rare.
+They employ NSM models originating from the fast-formation channel with short delay times ($\sim$5 Myr).
+We have added a short discussion towards the end of section 2.2.
+
 \begin{tcolorbox}[colback={lightgray}]   
@@
 
+\noindent\textbf{DS note (01 Jan 2024)}
+Here is my response to the referee -- feel free to edit:
+
+Thanks for making this distinction.
+It's correct that r-process material can be produced through alternative means, and thus we aren't fully investigating the source of all r-process material in this system.
+We have added some wording at the top of section 3 to emphasize that in this paper, we are only looking at r-process material from the NSM, which provides a lower limit.
+We also want to emphasize that we are indeed considering metal enrichment from Pop III and Pop II stars, but it is a general field in our simulation which includes more than just r-process material.
+
+The only group of stars enriched solely by Pop III stars will be the second generation of stars whose natal gas was not enriched by metal-enriched stars.
+This corresponds to the initial starburst of the galaxy, and is extremely metal-poor.
+Using a Kroupa IMF, we find that $\sim$40\% of stars formed at this early time would still be alive today.
+For a living stellar mass of 3000 \Ms, this would require an initial star formation event producing 7500 \Ms, which falls right in the middle of our stellar masses.
+
 \begin{tcolorbox}[colback={lightgray}] 
@@
 \end{tcolorbox}
+
+Apologies, we have corrected this.
+
+\
 

### 2024-01-01 NSM_Skinner_Wise/NSM_mixing.tex
Referee response -- just need final approval

@@
 
-The motivation for this work comes from the r-process enriched stars in Ret II, an ultrafaint dwarf (UFD) galaxy which serves as an ideal laboratory for studying early universe star formation.
+The motivation for this work comes from the r-process enriched stars in \textbf{\textit{Reticulum II (Ret II)}}, an ultrafaint dwarf (UFD) galaxy which serves as an ideal laboratory for studying early universe star formation.
 These systems typically form most of their stars early in the universe, before reionization was able to suppress star formation \citep{Weisz14}.
@@
 For a galaxy like Ret II, a NSM would have had to occur within 500 Myr to allow for ample time for thorough mixing to take place within the halo \citep{Simon23}.
-Delay times of 10, 100, and 300 Myr are short, but are not completely out of the realm of possibilities, and allow us to see how a NSM affects subsequent star formation at this early point in time.}
+Delay times of 10, 100, and 300 Myr are short, but are not completely out of the realm of possibilities, and allow us to see how a NSM affects subsequent star formation at this early point in time.} \textbf{\textit{Short delay times for these systems may be possible, yet rare, if the system has a low natal kick and undergoes a common envelope phase.
+Through this fast-formation channel, a shorter delay time has been studied with minimum delay times ranging from 0.1 Myr to 10 Myr \citep{Belczynski01, Dominik12, Belczynski18,Jeon21}.}}
 
@@
 In \S \ref{sec:energy_vary} and \S \ref{sec:time_vary}, we describe the explosion energy variation runs and the delay time variation runs.
+\textbf{\textit{When we discuss the r-process metallicities, we are only considering r-process material from the NSM.
+In this sense, we are looking at the lower-bound of r-process material in our system as we are not accounting for any r-process material produced via Population III or Population II stars.}}
 

### 2024-01-05 referee2/referee_response.tex
Minor wording revisions

--- 2023-10-31 referee2/referee_response.tex
@@
 
-We thank the referee for returning comments back to us. We will address the issues below and have boldfaced any changes made to the manuscript.
+We thank the referee for returning comments back to us.
+We will address the issues below and have \textit{\textbf{boldfaced and italicized}} any changes made to the manuscript to differentiate from the \textbf{boldfaced} changes made to the manuscript in the first revision cycle.
 
@@
 
-\noindent\textbf{JHW notes}
-\begin{itemize}
-  \item The intro of \href{https://ui.adsabs.harvard.edu/abs/2019ApJ...878L..12S/abstract}{Safarzadeh \& Berger (2019)} has some good information about constraining the minimum merger time.
+% \noindent\textbf{JHW notes}
+% \begin{itemize}
+%   \item The intro of \href{https://ui.adsabs.harvard.edu/abs/2019ApJ...878L..12S/abstract}{Safarzadeh \& Berger (2019)} has some good information about constraining the minimum merger time.
 The merger time distribution can be modeled as a power-law $dN/dt_{\rm merge} \propto t^\Gamma$, where $\Gamma$ is between --1.5 and --1.
 This comes from the initial binary separation distribution, which is steeper if the binary goes through a common envelope phase, meaning that there will be more close binaries in this case.
-  \item Also see \href{https://arxiv.org/abs/1812.10065}{Belczynski et al.
+%   \item Also see \href{https://arxiv.org/abs/1812.10065}{Belczynski et al.
 (2018)}, especially their Figures 7--10.
@@
 I'm not sure whether this paper was even published, but we can still cite it.
-  \item I would look for more references on the minimum time constraints, not just about Ret II.
+%   \item I would look for more references on the minimum time constraints, not just about Ret II.
 But we could argue that in particular cases where there has been a common envelope phase, one would except the resulting NS binary to have a small separation and thus merger time.
@@
 This only adds 10-20 Myr to the delay time, but it would make our 10 Myr delay times more reasonable.
-\end{itemize}
+% \end{itemize}
 
-\noindent\textbf{DS notes}
-\begin{itemize}
-  \item \href{https://iopscience.iop.org/article/10.1088/0004-637X/759/1/52/pdf}{Dominik et al.
+% \noindent\textbf{DS notes}
+% \begin{itemize}
+%   \item \href{https://iopscience.iop.org/article/10.1088/0004-637X/759/1/52/pdf}{Dominik et al.
 2015}: Figure 8 shows delay time distributions.
@@
 There are some models that have delay times of about 10 Myr.
-  \item \href{https://iopscience.iop.org/article/10.1086/319641/pdf}{Belczynski et al.
+%   \item \href{https://iopscience.iop.org/article/10.1086/319641/pdf}{Belczynski et al.
 2001}: They look at a different formation channel for NS binary systems, where a close binary neutron star system forms out of neutron stars that are not recycled (neither has been recycled by accretion).
 The merger times of these systems are on the lower end of $10^4$ - $10^8$ yr.
-  \item \href{https://www.aanda.org/articles/aa/pdf/2016/05/aa28193-16.pdf}{Mennekens et al.
+%   \item \href{https://www.aanda.org/articles/aa/pdf/2016/05/aa28193-16.pdf}{Mennekens et al.
 2016}: Their delay time is defined as the time between the formation of the binary system and the eventual formation of a NS-NS binary system plus the merger time.
-  \item \href{https://arxiv.org/pdf/2106.13383.pdf}{Jeon et al.
+%   \item \href{https://arxiv.org/pdf/2106.13383.pdf}{Jeon et al.
 2019}: They run zoom-in simulations studying the origin of MP r-II stars in UFDs.
 They assume that the merger occurs 5 Myr after the binary neutron star system forms, corresponding to the fast-merging channel.
-  \item Simon et al. 2023: They define the delay time as the time between the formation of the first stars and r-process nucleosynthesis and find for Ret II, it must be less than 500 Myr.
-  \item The referee is really focused on neutron stars from Pop III stars.
+%   \item Simon et al. 2023: They define the delay time as the time between the formation of the first stars and r-process nucleosynthesis and find for Ret II, it must be less than 500 Myr.
+%   \item The referee is really focused on neutron stars from Pop III stars.
 From what I've seen, there isn't a lot of work on neutron stars from Pop III stars and what the formation of those systems looked like.
@@
 Our response here may be along the lines of "it is possible (low natal-kicks, common envelope phase), but it is likely very rare" and we can cite some merger rates from Belczynski if they provide any.
-\end{itemize}
+% \end{itemize}
+
+% \noindent\textbf{JHW note (07 Dec 2023)}
+
+% I agree that we should add a sentence or two at the end of the next to last paragraph in Section 2.2, saying that a short delay time is possible yet rare if the system has a low natal kick and undergoes a common envelope phase, and cite those works.
+I really hope that the referee is appeased by this.
+
+% \noindent\textbf{DS note (01 Jan 2024)}
+% Below is my response to the referee -- feel free to edit:
+
+It is true that there is limited evidence that neutron stars originating from Pop III stars can merge within 100 Myr.
+This is clearly a field that will require much more investigation as we continue to probe to earlier and earlier times.
+However, some studies have investigated these short delay time scenarios.
+\citet{Belczynski18} study binary neutron star system formation and found that their models with lower minimum times have small or zero neutron star natal kicks, and thus undergo a highly efficient common envelope phase.
+This corresponds to a fast-formation channel for neutron star binary systems, and could possibly lead to shorter delay times.
+\citet{Jeon21} also investigate the origin of r-process enhanced stars in ultra-faint dwarf galaxies and agree that the exact origin of these NSMs is unknown, and likely very rare.
+They employ NSM models originating from the fast-formation channel with short delay times ($\sim$5 Myr).
+We have added a short discussion towards the end of Section 2.2.
 
@@
 
-\noindent\textbf{JHW notes}
-\begin{itemize}
-  \item This is a fair point.
+% \noindent\textbf{JHW notes}
+% \begin{itemize}
+%   \item This is a fair point.
 The only stars that will be solely enriched by Pop III stars would be the second generation of stars whose birth gas hasn't been enriched by metal-enriched stars.
-This would be the initial starburst of the galaxy, which should be extremely metal-poor $[Z/H] \sim -3$  Of those 80\% of the star formation in the early universe, we could use some star formation histories from the Birth of a Galaxy simulations to determine what fraction form in the initial burst.
-\end{itemize}
+This would be the initial starburst of the galaxy, which should be extremely metal-poor $[Z/H] \sim -3$.
+Of those 80\% of the star formation in the early universe, we could use some star formation histories from the Birth of a Galaxy simulations to determine what fraction form in the initial burst.
+% \end{itemize}
 
-\noindent\textbf{DS notes}
-\begin{itemize}
-  \item I see this point, but I am also thinking that we could revise some of our wording to say that we are only focused on the r-process enrichment from neutron star mergers.
+% \noindent\textbf{DS notes {(\color{purple} JHW responses})}
+% \begin{itemize}
+%   \item I see this point, but I am also thinking that we could revise some of our wording to say that we are only focused on the r-process enrichment from neutron star mergers.
 In that sense, we are seeing the "lower bound" of r-process enrichment for this type of system.
-  \item And are you talking about finding what fraction of the total amount of stars form in our galaxy in the initial burst? 
-  \item Also, it's not like we aren't considering metal enrichment form Pop III and Pop II stars, we just don't call the metallicity fraction enriched by those stars "r-process". 
-\end{itemize}
+%   \item {\color{purple} Agreed that this can be addressed by some rewording, saying that we aren't focused on the complete r-process enrichment history, but only the beginning, providing a lower limit.}
+%   \item And are you talking about finding what fraction of the total amount of stars form in our galaxy in the initial burst? 
+%   \item {\color{purple} I thought about this some more, and I don't think we should discuss the stellar mass formed in the early Universe because the galaxy hasn't stopped forming stars.
+The initial burst (looks like a single star particle with $M \simeq 10^3 M_\odot$) wouldn't be the right value to use because it's shortly after Pop III forms at $t \sim 200$ Myr and is not r-process enhanced.
+Also, the final mass wouldn't be valid either because the stars forming at late times could be r-enhanced by Pop II stars.}
+%   \item {\color{purple} But as a discussion point, we could use that 3000\Ms value given by the referee and convert it into a stellar mass at these redshifts.
+I've pushed a Jupyter notebook that calculates what fraction of these stars would still be alive today, and it's $\sim$40\%.
+So the star formation event that formed those 3000\Ms low-mass stars is 7500\Ms, which is right in the middle of our stellar masses.
+This is a little hand wavy, but I think it's good to point out.}
+%   \item Also, it's not like we aren't considering metal enrichment form Pop III and Pop II stars, we just don't call the metallicity fraction enriched by those stars "r-process".
+%   \item {\color{purple} Exactly.  I think we should emphasize this fact in the response, but I don't think we need to add anything to the paper about it.}
+% \end{itemize}
+
+% \noindent\textbf{DS note (01 Jan 2024)}
+% Here is my response to the referee -- feel free to edit:
+
+Thank you for making this distinction.
+We agree that r-process material can be produced through alternative means, and thus we are not fully investigating the source of all r-process material in this system.
+We have added a statement at the top of Section 3 to emphasize that in this paper, we are only looking at r-process material from the NSM, which provides a lower limit.
+We also want to emphasize that we are indeed considering metal enrichment from Pop III and Pop II stars, but it is a general field in our simulation which includes more than just r-process material.
+
+The only group of stars enriched solely by Pop III stars will be the second generation of stars whose natal gas was not enriched by metal-enriched stars.
+This corresponds to the initial starburst of the galaxy, and is extremely metal-poor.
+Using a Kroupa IMF, we find that $\sim$40\% of stars formed at this early time would still be alive today.
+For a living stellar mass of 3,000 \Ms, this would require an initial star formation event producing 7,500 \Ms, which falls right in the middle of our stellar masses.
 

### 2024-01-05 NSM_Skinner_Wise/NSM_mixing.tex
Minor wording revisions

@@
 \textbf{\textit{When we discuss the r-process metallicities, we are only considering r-process material from the NSM.
-In this sense, we are looking at the lower-bound of r-process material in our system as we are not accounting for any r-process material produced via Population III or Population II stars.}}
+In this sense, we are presenting the lower-bound of r-process material in our system as we are not accounting for any r-process material produced via core-collapse SNe from Pop III and Pop II stars.}}
 
